\RequirePackage[l2tabu]{nag}
\documentclass[pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=12pt, a4paper]{scrartcl}
\input{preamble/packages}
\input{preamble/redac}
\input{preamble/math_basics}
\input{preamble/math_mine}
\usepackage{bbm}
\usepackage{makecell}

\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}

%I find these settings useful in draft mode. Should be removed for final versions.
	%Which line breaks are chosen: accept worse lines, therefore reducing risk of overfull lines. Default = 200.
	%\tolerance=2000
	%Accept overfull hbox up to...
	\hfuzz=2cm
	%Reduces verbosity about the bad line breaks.
	\hbadness 5000
	%Reduces verbosity about the underful vboxes.
	\vbadness=1300

\linenumbers

\title{Two principles for two-person social choice \thanks{Earlier versions of this paper have been presented at CRESE, Université de Franche-Comté and CMSS, the University of Auckland. We thank both institutions. We also thank Miguel Ballester, Sylvain Béal, Danilo Santa Cruz Coelho, John Hillas, Jean-François Laslier, Clemens Puppe, Arkadii Slinko and Yves Sprumont for useful exchanges we had.}}
\author[*]{Olivier Cailloux}
\author[**]{Matías Núñez}
\author[*]{M. Remzi Sanver}
\affil[*]{Université Paris-Dauphine, PSL Research University, CNRS, LAMSADE, 75016 Paris, France.}
\affil[**]{CREST, CNRS, École Polytechnique, GENES, ENSAE Paris, Institut Polytechnique de Paris, 91120 Palaiseau, France.}
\date{}

\hypersetup{
	pdfsubject={},
	pdfkeywords={},
}

\begin{document}
\maketitle

\begin{abstract}
    We consider two-person ordinal collective choice from an axiomatic perspective. We identify two principles: minimal Rawlsianism (the chosen alternatives belong to the upper-half of both individuals’ preferences) and the equal loss principle (the chosen alternatives ensure that both individuals concede “as equally as possible” from their highest ranked alternative). The equal loss principle has variants of different strength, depending on the precise definition of “as equally as possible”. We consider all prominent ordinal two-person social choice rules of the literature and explore which of these principles they satisfy. Moreover, we show that minimal Rawlsianism is logically incompatible with one version of the equal loss principle that we call the minimal dispersion principle. On the other hand, there are social choice rules that satisfy the Rawlsian minimal dispersion principle where the minimal dispersion principle is restricted to alternatives within the upper-half of both individuals’ preferences.
\end{abstract}

\section{Introduction (submitted)}
\label{sec:intros}
Two-person discrete social choice models allow a specific interpretation of collective decision making: bargaining over a finite set of alternatives. Since the seminal model of \citet{Nash1950}, for a long time, bargaining problems were formulated by assuming a convex set of alternatives. However, there are many instances where bargaining takes place over a finite set of alternatives. Thus, this simplifying assumption of \citeauthor{Nash1950} excludes several real-life situations. 

\Citet{Mariotti1998} is among the first to relax this assumption by characterizing the Nash solution for a finite set of alternatives. His approach is followed by \citet{nagahisa2002axiomatization} who, again in a finite setting, characterize the solution of \citet{kalai1975other}. Both characterizations are built in a cardinal framework. 
 
An ordinal framework of two-person finite bargaining problems is presented by \citet{BramsKilgour2001} who introduce and analyze an ordinal solution, namely \textit{fallback bargaining}, that is based on compromising where each of the two bargainers begins by claiming the best outcome with respect to his ranking of alternatives. When the claims of the two bargainers differ, they continue by falling back, in lockstep, to lower ranked alternatives until a mutually (hence unanimously) agreed outcome is found. A characterization of fallback bargaining is provided by \citet{de2012reason}. As this solution is presented in a model that does not admit a disagreement point, fallback bargaining is rather an arbitration rule in the sense of \citet{Sprumont1993} than being a bargaining solution. An analysis of fallback bargaining in a model with a disagreement point is made by \citet{KibrisSertel2007} who rebaptize the solution as \textit{unanimity compromise} and define several variants of it.\footnote{They also observe that one of these variants, namely the imputational compromise, is the finite version of the equal length rule by \citet{thomson2019equal}. The imputational compromise is further studied by \citet{ConleyWilkie2012}.} In a recent paper, \citet{barbera2022compromising} use the term unanimity compromise in a framework with no disagreement point to refer to fallback bargaining in the sense of \citet{BramsKilgour2001}. We adopt their terminology, to avoid proposing a bargaining solution without a disagreement outcome.

As a matter of fact, the compromising approach that underlies unanimity compromise was originally used to design voting rules in settings with more than two individuals with the required support varying from unanimity to simple majority, such as the \textit{Kant-Rawls Social Compromise} by \citet{HurwiczSertel1997} and the \textit{majoritarian compromise} by \citet{sertel1999majoritarian}. It also paved the way to new axioms for social choice, such as \textit{majoritarian approval} and \textit{majoritarian optimality} as well as \textit{efficiency in the degree of compromise} by \citet{ozkal2004efficiency}.
\citet{merlin2019compromise} present a recent comprehensive analysis of voting rules and axioms based on this compromising idea.

A closer look at this compromising idea and in particular at unanimity compromise reveals a principle for two-person social choice. \Citet{Sprumont1993} qualifies arbitration rules that maximize the welfare of the least happy individual as being \textit{Rawlsian}. \citet{congar2012characterization} characterize the Rawlsian principle within the framework of social welfare functions. For social choice rules, \citet{BramsKilgour2001} establish the equivalence between the Rawlsian principle and unanimity compromise. Moreover, they show that every individual ranks a unanimity compromise outcome in the upper-half of his ranking. Thus, at every preference profile, there is an alternative that both individuals rank in the upper-half of their preference. In other words, the least happy individual of the society can always be granted a welfare within the first half of his preference. We qualify a two-person social choice rule that complies with this possibility as \textit{minimally Rawlsian}.%
\footnote{In a two-person collective choice framework with an interpretation that is more specific than ours, \citet{Clippel} call this condition the \textit{minimal satisfaction test}.}

\Citet{cailloux2022compromising} propose a different conception of compromising based on an \textit{equal loss principle} that favors outcomes where every individual concedes as equally as possible from his highest ranked alternative. They show that several two-person social choice rules fail this principle.

Although the minimal Rawlsian and equal loss principles cover many of the two-person social choice rules, the literature is missing an axiomatic analysis of these rules from this perspective, an observation which forms the subject matter of our paper. We consider the following rules, where $m$ is the number of alternatives.
\begin{itemize}
	\item Unanimity compromise, as defined by \citet{BramsKilgour2001} (under the name of fallback bargaining).
	\item The \textit{veto-rank rule} where, for $m$ odd, each individual vetoes $(m - 1) / 2$ alternatives and ranks the remaining $(m+1) / 2$. The outcome is the alternatives with the minimal sum of ranks among those that have not been vetoed.
	\item The \textit{shortlisting rule} where, for $m$ odd, one individual selects her best $(m+1) / 2$ alternatives and the rule picks the best alternative of the other individual out of that shortlist.
	\item The class of \textit{Pareto-and-veto rules} where each individual $i$ vetoes a fixed number $v_i$ of alternatives with $v_1 + v_2$ being lower than $m$. The outcome is the set of Pareto optimal alternatives that are not vetoed. 
\end{itemize}

The veto-rank rule and the shortlisting rule are used for the selection of arbitrators and their strategic aspects are comprehensively analyzed by \citet{Clippel}% 
\footnote{\Citet{Clippel} present the shortlisting mechanism, whose equilibrium outcome corresponds to what we call the shortlisting rule.}. Our class of Pareto-and-veto rules generalizes the Pareto-and-veto rules analyzed by \citet{laslier2021solution} which impose $v_1$ + $v_2$ = $m-1$. These rules we consider cover most of the ordinal two-person social choice rules in the literature. The literature also admits various interesting real-life procedures expressed as extensive form games, such as those in \citet{anbarci1993noncooperative, anbarci2006finite} and \citet{barbera2022compromising}. However, as shown in these papers, the subgame perfect equilibrium outcomes of these games are always among the unanimity compromise alternatives. 

A rule of specific interest is the Pareto-and-veto rule that gives the highest equal veto power to both individuals. This rule yields all Pareto efficient alternatives that are in the upper half of both individuals. In fact, it can be expressed the union all Pareto efficient and minimally Rawlsian rules. Unanimity compromise, the veto-rank rule and the shortlisting rule are all sub correspondences of this rule, hence they are minimally Rawlsian. When $m$ is odd, Within the class of Pareto-and-veto rules, the one with highest equal veto power is unique in being minimally Rawlsian while when $m$ is even, there are two other that give the highest almost equal veto power to both individuals.

The equal loss principle we consider favors outcomes that have the same rank for both individuals. Without imposing Pareto optimality separately, this principle may lead to Pareto dominated outcomes. Thus, we consider a Pareto efficient version that favors, among the Pareto optimal outcomes, the one that has the same rank for both individuals. Note that such an alternative, if it exists, will be unique. We define two versions of the Paretian equal loss principle, one being stronger than the other. The stronger version requires that the Pareto optimal alternative that has the same rank for both individuals must be uniquely chosen. Under the weaker version, it suffices that this alternative be among the outcomes. The veto-rank rule and the shortlisting rule both fail the weak (hence strong) version of the Paretian equal loss principle. While Pareto-and-veto rules that endow individuals with a veto power that does not exceed $\floor{\frac{m}{2}}$ satisfy the weak Paretian equal loss principle, all of them fail the strong version. On the other hand, unanimity compromise satisfies the strong Paretian equal loss principle, thus showing that this principle is compatible with being minimally Rawlsian.
 
Within the spirit of equal loss, we propose the \textit{minimal dispersion principle} as another strengthening of the (weak) Paretian equal loss principle. The \textit{dispersion} of an alternative is the difference between the two ranks at which is it placed. The minimal dispersion principle requires that an alternative whose dispersion is minimal is among the outcomes. Not only unanimity compromise fails this principle, but the minimal dispersion principle turns out to be logically incompatible with the minimal Rawlsian principle. As a result, among the social choice rules we consider, the only candidates to satisfy the minimal dispersion principle are the Pareto-and-veto rules that fail the minimal Rawlsian principle. As a matter of fact, those that endow individuals with a veto power that does not exceed a third of the available alternatives turn out to satisfy the minimal dispersion principle.\footnote{Recall that this upper bound is a half for the satisfaction of the (weaker) Paretian equal loss principle.} Nevertheless, these Pareto-and-veto rules fail two stronger versions of the minimal dispersion principle, one that requires to pick all alternatives with minimal dispersion and the other that requires to pick only alternatives with minimal dispersion. As a result, we define the minimal dispersion rule which, at every preference profile, picks precisely the alternatives with minimal dispersion.\footnote{
\label{ft:equalareas}
In a framework with a disagreement outcome, \citet{KibrisSertel2007} argue that the finite version of the \textit{equal area rule} \citep{thomson1994cooperative} minimizes the difference between losses with respect to individually rational alternatives. They also show that this rule differs from their unanimity compromise. In our framework without a disagreement outcome, the equal area rule is equivalent to our minimal dispersion rule.}

Given the incompatibility between the two principles, we introduce the Rawlsian minimal dispersion principle that requires the outcome to contain the Rawlsian alternatives whose loss vectors have minimal dispersion. It turns out that it is failed by all social choice rules we consider, except the Pareto-and-veto rule that gives the highest equal veto power to both individuals. The satisfaction is at the expense of resoluteness, since this rule picks every Pareto efficient alternative within the first half. It is thus natural to seek for a stronger principle that imposes more resoluteness. To this end, we define the strong Rawlsian minimal dispersion principle that requires the outcome to lie within the Rawlsian alternatives whose loss vectors have minimal dispersion. No rule that we have examined satisfies this principle. Therefore, we define the strong Rawlsian minimal dispersion rule as the least resolute rule that satisfies this principle. This new rule appears as a reasonable compromise to satisfy the two main principles we analyze, namely that of being minimally Rawlsian and that of favoring small dispersion alternatives. Moreover, it is also reasonably resolute as it never picks more than two alternatives.

\Cref{sec:basic} introduces the basic notions and notation. \Cref{sec:minprinc,sec:eqprinc} are devoted to the minimal Rawlsian and equal loss principles, respectively. \Cref{sec:reconc} introduces the Rawlsian minimal dispersion principle. \Cref{sec:concl} makes some concluding remarks.

\section{Introduction (prop 1)}
\label{sec:intro}
Since the classic model of \citet{Nash1950}, most of the literature in bargaining assumes the existence of a convex set of alternatives. However, there are many instances where convexity need not hold. For instance, when bargaining takes place over a finite set of alternatives and lotteries are not admissible, such as in a legal setting, the assumption of convexity is not relevant.\footnote{Remark that the convexity assumption in the Nash bargaining problem may be natural if the bargaining solution admits lotteries on a finite set of alternatives. But
then, preferences should be cardinal. We focus here on ordinal preferences - we thank the associate editor for pointing this out.} Our axiomatic approach tries to fill this gap: that is, it presents some axioms that help understanding bargaining over a finite set of alternatives (or two-person discrete social choice).

Within the paper, we often refer to the most well-known rules in this environment: the Unanimity compromise, the veto-rank, the shortlisting and the Pareto-and-veto ones. We refer the reader to the review of the literature for a description of these rules.

Our first axiom is the \textit{equal loss principle} that favors outcomes that have the same rank for both individuals, out of fairness. However, without imposing Pareto optimality separately, this principle may lead to Pareto dominated outcomes. Thus, we consider a Pareto efficient version that favors, among the Pareto optimal outcomes, the one that has the same rank for both individuals. Note that such an alternative, if any, will be unique. We define two versions of the Paretian equal loss principle, one being stronger than the other. The stronger version requires that the Pareto optimal alternative that has the same rank for both individuals is uniquely chosen. Under the weaker version, it suffices that this alternative is among the outcomes. The veto-rank rule and the shortlisting rule both fail the weak (hence strong) version of the Paretian equal loss principle. While Pareto-and-veto rules that endow individuals with a veto power that does not exceed $\floor{\frac{m}{2}}$ satisfy the weak Paretian equal loss principle, all of them fail the strong version. On the other hand, unanimity compromise satisfies the strong Paretian equal loss principle, thus showing that this principle is compatible with being minimally Rawlsian.

Within the spirit of equal loss, we also propose the \textit{minimal dispersion principle} as another strengthening of the (weak) Paretian equal loss principle. The \textit{dispersion} of an alternative is the difference between the two ranks at which is it placed. The minimal dispersion principle requires that an alternative whose dispersion is minimal is among the outcomes. Not only unanimity compromise fails this principle, but the minimal dispersion principle turns out to be logically incompatible with the minimal Rawlsian principle. As a result, among the social choice rules we consider, the only candidates to satisfy the minimal dispersion principle are the Pareto-and-veto rules that fail the minimal Rawlsian principle. As a matter of fact, those that endow individuals with a veto power that does not exceed a third of the available alternatives turn out to satisfy the minimal dispersion principle.\footnote{Recall that this upper bound is a half for the satisfaction of the (weaker) Paretian equal loss principle.} Nevertheless, these Pareto-and-veto rules fail two stronger versions of the minimal dispersion principle, one that requires to pick all alternatives with minimal dispersion and the other that requires to pick only alternatives with minimal dispersion. As a result, we define the minimal dispersion rule which, at every preference profile, picks precisely the alternatives with minimal dispersion.\footnote{
In a framework \label{ft:equalarea} with a disagreement outcome, \citet{KibrisSertel2007} argue that the finite version of the \textit{equal area rule} \citep{thomson1994cooperative} minimizes the difference between losses with respect to individually rational alternatives. They also show that this rule differs from their unanimity compromise. In our framework without a disagreement outcome, the equal area rule is equivalent to our minimal dispersion rule.}

Given the incompatibility between the two principles, we introduce the Rawlsian minimal dispersion principle that requires the outcome to contain the Rawlsian alternatives whose loss vectors have minimal dispersion. It turns out that it is failed by all social choice rules we consider, except the Pareto-and-veto rule that gives the highest equal veto power to both individuals. The satisfaction is at the expense of resoluteness, since this rule picks every Pareto efficient alternative within the first half. It is thus natural to seek for a stronger principle that imposes more resoluteness. To this end, we define the strong Rawlsian minimal dispersion principle that requires the outcome to lie within the Rawlsian alternatives whose loss vectors have minimal dispersion. No rule that we have examined satisfies this principle. Therefore, we define the strong Rawlsian minimal dispersion rule as the least resolute rule that satisfies this principle. This new rule appears as a reasonable compromise to satisfy the two main principles we analyze, namely that of being minimally Rawlsian and that of favoring small dispersion alternatives. Moreover, it is also reasonably resolute as it never picks more than two alternatives.

\Cref{sec:rev} reviews the most closely related literature and \Cref{sec:basic} introduces the basic notions and notation. \Cref{sec:lit} presents several social choice rules. \Cref{sec:minprinc,sec:eqprinc} are devoted to the minimal Rawlsian and equal loss principles, respectively. \Cref{sec:reconc} introduces the Rawlsian minimal dispersion principle. \Cref{sec:concl} makes some concluding remarks.

\section{Review of literature \label{sec:rev}}
While the literature on bargaining is large, the one with finitely many alternatives is relatively scant. We review here the main works in the latter field.
\Citet{Mariotti1998} is among the first to relax this assumption by characterizing the Nash solution for a finite set of alternatives. His approach is followed by \citet{nagahisa2002axiomatization} who, again in a finite setting, characterize the solution of \citet{kalai1975other}. Both characterizations are built in a cardinal framework. 

An ordinal framework of two-person finite bargaining problems is presented by \citet{BramsKilgour2001} who introduce and analyze an ordinal solution, namely \textit{fallback bargaining}, that is based on compromising where each of the two bargainers begins by claiming the best outcome with respect to his ranking of alternatives. When the claims of the two bargainers differ, they continue by falling back, in lockstep, to lower ranked alternatives until a mutually (hence unanimously) agreed outcome is found. A characterization of fallback bargaining is provided by \citet{de2012reason}. As this solution is presented in a model that does not admit a disagreement point, fallback bargaining is rather an arbitration rule in the sense of \citet{Sprumont1993} than being a bargaining solution. An analysis of fallback bargaining in a model with a disagreement point is made by \citet{KibrisSertel2007} who rebaptize the solution as \textit{unanimity compromise} and define several variants of it.\footnote{They also observe that one of these variants, namely the imputational compromise, is the finite version of the equal length rule by \citet{thomson2019equal}. The imputational compromise is further studied by \citet{ConleyWilkie2012}.} In a recent paper, \citet{barbera2022compromising} use the term unanimity compromise in a framework with no disagreement point to refer to fallback bargaining in the sense of \citet{BramsKilgour2001}. We adopt their terminology, to avoid proposing a bargaining solution without a disagreement outcome.

As a matter of fact, the compromising approach that underlies unanimity compromise was originally used to design voting rules in settings with more than two individuals with the required support varying from unanimity to simple majority, such as the \textit{Kant-Rawls Social Compromise} by \citet{HurwiczSertel1997} and the \textit{majoritarian compromise} by \citet{sertel1999majoritarian}. It also paved the way to new axioms for social choice, such as \textit{majoritarian approval} and \textit{majoritarian optimality} as well as \textit{efficiency in the degree of compromise} by \citet{ozkal2004efficiency}.
\citet{merlin2019compromise} present a recent comprehensive analysis of voting rules and axioms based on this compromising idea.

A closer look at this compromising idea and in particular at unanimity compromise reveals a principle for two-person social choice. \Citet{Sprumont1993} qualifies arbitration rules that maximize the welfare of the least happy individual as being \textit{Rawlsian}. \citet{congar2012characterization} characterize the Rawlsian principle within the framework of social welfare functions. For social choice rules, \citet{BramsKilgour2001} establish the equivalence between the Rawlsian principle and unanimity compromise. Moreover, they show that every individual ranks a unanimity compromise outcome in the upper-half of his ranking. Thus, at every preference profile, there is an alternative that both individuals rank in the upper-half of their preference. In other words, the least happy individual of the society can always be granted a welfare within the first half of his preference. We qualify a two-person social choice rule that complies with this possibility as \textit{minimally Rawlsian}.%
\footnote{In a two-person collective choice framework with an interpretation that is more specific than ours, \citet{Clippel} call this condition the \textit{minimal satisfaction test}.}

\Citet{cailloux2022compromising} propose a different conception of compromising based on an \textit{equal loss principle} that favors outcomes where every individual concedes as equally as possible from his highest ranked alternative. They show that several two-person social choice rules fail this principle.

Although the minimal Rawlsian and equal loss principles cover many of the two-person social choice rules, the literature is missing an axiomatic analysis of these rules from this perspective, an observation which forms the subject matter of our paper. We consider the following rules, where $m$ is the number of alternatives.
\begin{itemize}
	\item Unanimity compromise, as defined by \citet{BramsKilgour2001} (under the name of fallback bargaining).
	\item The \textit{veto-rank rule} where, for $m$ odd, each individual vetoes $(m - 1) / 2$ alternatives and ranks the remaining $(m+1) / 2$. The outcome is the alternatives with the minimal sum of ranks among those that have not been vetoed.
	\item The \textit{shortlisting rule} where, for $m$ odd, one individual selects her best $(m+1) / 2$ alternatives and the rule picks the best alternative of the other individual out of that shortlist.
	\item The class of \textit{Pareto-and-veto rules} where each individual $i$ vetoes a fixed number $v_i$ of alternatives with $v_1 + v_2$ being lower than $m$. The outcome is the set of Pareto optimal alternatives that are not vetoed. 
\end{itemize}

The veto-rank rule and the shortlisting rule are used for the selection of arbitrators\footnote{\Citet{Clippel} present the shortlisting mechanism, whose equilibrium outcome corresponds to what we call the shortlisting rule.} and their strategic aspects are comprehensively analyzed by \citet{Clippel}. Our class of Pareto-and-veto rules generalizes the Pareto-and-veto rules analyzed by \citet{laslier2021solution} which impose $v_1$ + $v_2$ = $m-1$. These rules we consider cover most of the ordinal two-person social choice rules in the literature. The literature also admits various interesting real-life procedures expressed as extensive form games, such as those in \citet{anbarci1993noncooperative, anbarci2006finite} and \citet{barbera2022compromising}. However, as shown in these papers, the subgame perfect equilibrium outcomes of these games are always among the unanimity compromise alternatives. 

\newpage
\section{Introduction (prop 2)}
\label{sec:introp}
Two-person discrete social choice models allow a specific interpretation of collective decision making: bargaining over a finite set of alternatives.
In ordinal settings including no disagreement point, such rules are called arbitration rules by \citet{Sprumont1993}. This article is interested in analyzing such rules through the lens of two principles that permit to compare and distinguish them.

\citet{Sprumont1993} qualifies arbitration rules that maximize the welfare of the least happy individual as being \textit{Rawlsian}. For social choice rules, \citet{BramsKilgour2001} showed that at every preference profile, there is an alternative that both individuals rank in the upper-half of their preference. In other words, the least happy individual of the society can always be granted a welfare within the first half of his preference. 
We qualify a two-person social choice rule that complies with this possibility as \textit{minimally Rawlsian}.

\Citet{cailloux2022compromising} propose a different conception of compromising based on an \textit{equal loss principle} that favors outcomes where every individual concedes as equally as possible from his highest ranked alternative. 

Although the minimal Rawlsian and equal loss principles cover many of the two-person social choice rules, the literature is missing an axiomatic analysis of these rules from this perspective, an observation which forms the subject matter of our paper.

We now describe the rules that we consider, namely, Unanimity compromise; Veto-rank; Shortlisting and the Pareto-and-veto rules.
They cover most of the ordinal two-person social choice rules in the literature. 

In the \textit{unanimity compromise} \citep{BramsKilgour2001} rule, each of the two bargainers begins by claiming the best outcome with respect to his ranking of alternatives. When the claims of the two bargainers differ, they continue by falling back, in lockstep, to lower ranked alternatives until a mutually (hence unanimously) agreed outcome is found. 

The next two rules are used for the selection of arbitrators \citep{Clippel}.
The \textit{veto-rank rule} where, for a number of alternatives $m$ being odd, each individual vetoes $(m - 1) / 2$ alternatives and ranks the remaining $(m+1) / 2$. The outcome is the alternatives with the minimal sum of ranks among those that have not been vetoed.
The \textit{shortlisting rule} where, for $m$ odd, one individual selects her best $(m+1) / 2$ alternatives and the rule picks the best alternative of the other individual out of that shortlist.

Finally, we consider the class of \textit{Pareto-and-veto rules} where each individual $i$ vetoes a fixed number $v_i$ of alternatives with $v_1 + v_2$ being at most $m - 1$. The outcome is the set of Pareto optimal alternatives that are not vetoed.
This class of rules generalizes the Pareto-and-veto rules analyzed by \citet{laslier2021solution} which impose $v_1$ + $v_2$ = $m-1$. 

A rule of specific interest is the Pareto-and-veto rule that gives the highest equal veto power to both individuals. This rule yields all Pareto efficient alternatives that are in the upper half of both individuals. In fact, it can be expressed as the union all Pareto efficient and minimally Rawlsian rules. Unanimity compromise, the veto-rank rule and the shortlisting rule are all sub correspondences of this rule, hence they are minimally Rawlsian. Within the class of Pareto-and-veto rules, the only rule being minimally Rawlsian is the one with highest equal veto power (or almost equal veto power for $m$ even).

The equal loss principle we consider favors outcomes that have the same rank for both individuals. Without imposing Pareto optimality separately, this principle may lead to Pareto dominated outcomes. Thus, we consider a Pareto efficient version that favors, among the Pareto optimal outcomes, the one that has the same rank for both individuals. Note that such an alternative, if it exists, will be unique. We define two versions of the Paretian equal loss principle, one being stronger than the other. The stronger version requires that the Pareto optimal alternative that has the same rank for both individuals must be uniquely chosen. Under the weaker version, it suffices that this alternative be among the outcomes. The veto-rank rule and the shortlisting rule both fail the weak (hence strong) version of the Paretian equal loss principle. While Pareto-and-veto rules that endow individuals with a veto power that does not exceed $\floor{\frac{m}{2}}$ satisfy the weak Paretian equal loss principle, all of them fail the strong version. On the other hand, unanimity compromise satisfies the strong Paretian equal loss principle, thus showing that this principle is compatible with being minimally Rawlsian.
 
Within the spirit of equal loss, we propose the \textit{minimal dispersion principle} as another strengthening of the (weak) Paretian equal loss principle. The \textit{dispersion} of an alternative is the difference between the two ranks at which is it placed. The minimal dispersion principle requires that an alternative whose dispersion is minimal is among the outcomes. Not only unanimity compromise fails this principle, but the minimal dispersion principle turns out to be logically incompatible with the minimal Rawlsian principle. As a result, among the social choice rules we consider, the only candidates to satisfy the minimal dispersion principle are the Pareto-and-veto rules that fail the minimal Rawlsian principle. As a matter of fact, those that endow individuals with a veto power that does not exceed a third of the available alternatives turn out to satisfy the minimal dispersion principle. Nevertheless, these Pareto-and-veto rules fail two stronger versions of the minimal dispersion principle, one that requires to pick all alternatives with minimal dispersion and the other that requires to pick only alternatives with minimal dispersion. As a result, we define the minimal dispersion rule which, at every preference profile, picks precisely the alternatives with minimal dispersion.

Given the incompatibility between the two principles, we introduce the Rawlsian minimal dispersion principle that requires the outcome to contain the Rawlsian alternatives whose loss vectors have minimal dispersion. It turns out that it is failed by all social choice rules we consider, except the Pareto-and-veto rule that gives the highest equal veto power to both individuals. The satisfaction is at the expense of resoluteness, since this rule picks every Pareto efficient alternative within the first half. It is thus natural to seek for a stronger principle that imposes more resoluteness. To this end, we define the strong Rawlsian minimal dispersion principle that requires the outcome to lie within the Rawlsian alternatives whose loss vectors have minimal dispersion. No rule that we have examined satisfies this principle. Therefore, we define the strong Rawlsian minimal dispersion rule as the least resolute rule that satisfies this principle. This new rule appears as a reasonable compromise to satisfy the two main principles we analyze, namely that of being minimally Rawlsian and that of favoring small dispersion alternatives. Moreover, it is also reasonably resolute as it never picks more than two alternatives.

\Cref{sec:basic} introduces the basic notions and notation. \Cref{sec:minprinc,sec:eqprinc} are devoted to the minimal Rawlsian and equal loss principles, respectively. \Cref{sec:reconc} introduces the Rawlsian minimal dispersion principle. \Cref{sec:concl} makes some concluding remarks.

\section{Basic notions and notation}
\label{sec:basic} 
Let $N = \set{1, 2}$ be a set of two individuals and $\allalts$ be a set of alternatives, with $\card{\allalts} = m\geq 2$. 
For each $i \in N$, we denote by $\ibar \in N \setminus \set{i}$  the other individual. Let $\powersetz{\allalts}$ denote the set of non-empty subsets of $\allalts$ and $\linors$ be the set of linear orders over $\allalts$. We let ${\prefi} \in \linors$ be the preference of individual $i \in N$ and $\prof = ({\prefi[1]}, {\prefi[2]}) \in \allprofs$ a preference profile. 
A social choice rule (SCR) is a correspondence $f: \allprofs → \powersetz{\allalts}$.
Viewing such functions as relations on $\allprofs × \allalts$, we can write $f \subseteq f'$ to denote a rule that “refines” $f'$, in the sense that $\forall \prof \in \allprofs: f(\prof) \subseteq f'(\prof)$. When $f \subseteq f'$ and $f ≠ f'$, we write $f \subsetneq f'$ and say that $f$ is a proper sub-correspondence of $f'$.

A SCR $f$ is anonymous iff, for any $({\prefi[1]}, {\prefi[2]}) \in \allprofs$, $f({\prefi[1]}, {\prefi[2]}) = f(\hspace{-0.6pt}{\prefi[2]}, {\prefi[1]}\hspace{-0.6pt})$ while $f$ is neutral iff for any permutation $\sigma$ over $\allalts$ and any profile $\prof \in \allprofs$, $\sigma \circ f(\prof) = f(\sigma \circ \prof)$.

Given $p, q \in \R$, let $\intvlz{q} = [0, q] \cap \N $ denote the interval of integers between $p$ and $q$ (throughout the article, $\N$ includes zero). The loss of individual $i$ at $\prof$ for alternative $x$ equals the number of alternatives that $i$ prefers to $x$: $\lprof(x)_i = \card{\set{y \in \allalts \suchthat y \prefi x}}$. The loss vector of $x$ at $\prof$ is denoted $\lprof(x)=(\lprof(x)_1, \lprof(x)_2) \in \lvs$. Given two loss vectors $l, l' \in \lvs$, $l$ is smaller than $l'$, denoted $l ≤ l'$, iff $l_i ≤ l'_i$ $\forall i$. We also write $l < l'$ when $l$ is strictly smaller than $l'$, meaning, smaller and different. 
Let $\min \lprof(x) = \min_{i \in N} \lprof(x)_i \in \N$, $\max \lprof(x) = \max_{i \in N} \lprof(x)_i \in \N$ 
and $\sum \lprof(x) = \sum_{i \in N} \lprof(x)_i$  respectively denote the minimal loss, the maximal one and the sum of the losses in $\lprof(x)$.
Let $\min \max \lprof = \min_{x \in \allalts} \max \lprof(x)$ denote the minimal (across alternatives) worst (across individuals) loss at $\prof$.

Let $\PE = \set{x \in \allalts \suchthat \nexists \: y \text{ s.t. } \lprof(y) < \lprof(x)}$ be the set of Pareto efficient alternatives at $\prof$.
The SCR $f$ satisfies the Pareto property iff it picks only Pareto efficient alternatives.
Let $\PEcl = \set{f: \allprofs → \powersetz{\allalts} \suchthat \forall \prof: f(\prof) \subseteq \PE}$ denote the class of SCRs satisfying the Pareto property.\footnote{We systematically use calligraphic letters to denote the class of rules satisfying a given property.}

In concordance with the ceiling established by Theorem 1 of \citet{BramsKilgour2001}, we use  “best half” to refer to the loss values up to $\khalf$, where $\lfloor x \rfloor$ denotes the greatest integer less than or equal to $x$.  For any profile $\prof \in \allprofs$, we let $H(\prof) = \set{x \in \allalts \suchthat \lprof(x) ≤ (\khalf, \khalf)}$ denote the set of alternatives reaching the best half of every individual’s preference, and $H^i(\prof) = \set{x \in \allalts \suchthat \lprof(x)_i ≤ \khalf}$ those that reach the best half of $i$’s preference. Given $\prof$ and a loss level $k$, define $U(\prof, k) = \set{x \in \allalts \suchthat \max \lprof(x) ≤ k}$ as the alternatives with a loss of at most $k$ for both individuals. 
It follows that $H(\prof) = U(\prof, \khalf)$.
An alternative receives unanimous support at level $k$ iff it belongs to $U(\prof, k)$. 
Note that the minimal worst loss $\min \max \lprof$ also represents the least loss level at which some alternative receives unanimous support; formally: $\min \max \lprof = \min \set{k \in \losses \suchthat U(\prof, k) ≠ \emptyset}$.

\section{SCRs in the literature}
\label{sec:lit}
We start by defining the SCRs of the literature that we analyze in the paper and giving some preliminary observations about these rules.

\textbf{Unanimity compromise or $\FB$} is the SCR that picks all alternatives with unanimous support at the minimal worst loss $\rhoP = \min_{x \in \allalts} \set{\max \lprof(x)}$; formally: $\FB(\prof) = U(\prof, \rhoP) = \argmin_{x \in \allalts} \set{\max \lprof(x)}$.
\begin{remark}
	\label{th:FBH}
	$\FB$ is anonymous and neutral. It satisfies the Pareto property. Moreover, $\forall \prof$, $\FB(\prof) \subseteq H(\prof)$. The final observation comes from the fact that $\forall \prof$, $\min_{x \in \allalts} \set{\max \lprof(x)} ≤ \khalf$, a consequence of the following proposition that is a restatement of \citet[Theorem 1]{BramsKilgour2001}. We include a proof for completeness.
\end{remark}

%\newtheoremstyle{proposition-then-small-style}%
%  {}
%  {}
%  {}{}%
%  {\bfseries}{}%
%  { }{\thmname{#1}\thmnumber{ #2}\normalfont\fontsize{10}{8}\selectfont\thmnote{ (#3)}}%
%\newtheoremstyle{proposition-then-small-style}%
%  {}
%  {}
%  {}{}%
%  {\bfseries\fontsize{10.25}{8}}{}%
%  { }{}%
%\theoremstyle{proposition-then-small-style}
%\newtheorem{proposition-then-small}[proposition]{Proposition}
%To fit on one line.
\fontsize{11.25}{1}
\begin{proposition}[\citeauthor{BramsKilgour2001}]
	\label{th:BKkhalf}
	$[\forall \prof, \exists x \in \allalts \suchthat \max \lprof(x) ≤ k] ⇔ k ≥ \khalf$.
\end{proposition}
\normalsize
\begin{proof}
	To prove the “only if” part, let $k < \khalf$ and consider the profile $\prof$ composed of an arbitrary ordering $\prefi$ over $\allalts$ and its inverse ordering ${\prefi[\ibar]} = {\prefiinv}$ and observe that $\min \max \lprof = \khalf > k$, where $\lprof=\{\lprof(x)\}_{x\in \allalts}$ stands for the loss vector at $\prof$.
	
	To prove the “if” part, let $k ≥ \khalf$. For any $\prof \in \allprofs$, we show that for some $x \in \allalts$, $\max \lprof(x) ≤ k$.
	Define $A = \set{a \in \allalts \suchthat 0 ≤ \lprof(a)_1 ≤ \khalf}$.
	Define $B = \set{a \in \allalts \suchthat \khalf < \lprof(a)_2 ≤ m - 1}$.
	Observe that $\card{A} = \khalf + 1$ and $\card{B} = (m - 1) - \khalf = (m - 1) - \khalfAlt = \khalfC ≤ \khalf$, thus, $\card{B} < \card{A}$.
	Thus, $\exists x \in A \setminus B$.
	And $\lprof(x)_1 ≤ \khalf$ (as $x \in A$) and $\lprof(x)_2 ≤ \khalf$ (as $x \notin B$).
	It follows that $\max \lprof(x) ≤ \khalf$.
\end{proof}

In the \textbf{veto-rank rule} or $\VR$, each individual vetoes her worst $\floor{\frac{m - 1}{2}}$ alternatives, and the Borda winners among the non vetoed alternatives are picked: $\VR(\prof) = \argmin_{H(\prof)} \sum \lprof = \set{x \in H(\prof) \suchthat \forall y \in H(\prof): \sum \lprof(x) ≤ \sum \lprof(y)}$.

In the \textbf{shortlisting rule} or $\SL$, the best alternative of individual $1$  that is not among the worst $\floor{\frac{m - 1}{2}}$ alternatives of individual $2$  and the best alternative of $2$ that is not among the worst $\floor{\frac{m - 1}{2}}$ alternatives of $1$ are selected: $SL(\prof) = \cup_{i \in N} (\argmin_{x \in H^i(\prof)} \lprof(x)_{\ibar})$.

Both $\VR$ and $\SL$ are defined in \citet{Clippel} for $m$ odd only.

\begin{remark}
	\label{th:VRSLH}
Both	$\VR$ and $\SL$ are anonymous and neutral. They satisfy the Pareto property. Moreover, $\forall \prof$, $\VR(\prof) \subseteq H(\prof)$ and $\SL(\prof)\subseteq H(\prof)$.
\end{remark}

\begin{remark}\label{th:different}
There is some $\prof$ such that $\FB(\prof) \cap \VR(\prof) = \emptyset, \FB(\prof) \cap \SL(\prof) = \emptyset$ and $\VR(\prof) \cap \SL(\prof) = \emptyset$. Consider the profile $\prof = (\pref_1, \pref_2)$ defined as
	\begin{equation}
		\label{eq:distinct}
		\begin{array}{l @{:\hskip 2em} *{7}l | *{6}l}
			\pref_1&a&b&c&d&e&f&g&h&i&j&k&l&m\\
			\pref_2&g&h&i&d&b&j&a&c&e&f&k&l&m\\
		\end{array},
	\end{equation}
	where alternatives are ranked from left to right and the bar shows the “half” position.
	The remark is proven by noting that $\FB(\prof) = \set{d}$, $\VR(\prof) = \set{b}$ and $\SL(\prof) = \set{a, g}$.
\end{remark}

The class of \textbf{Pareto-and-veto rules}, $\PVcl$, contains rules parametrized by $v_1, v_2 \in \intvlz{m - 1}$ with $v_1 + v_2 ≤ m - 1$ where $v_i$ represents the number of alternatives vetoed by individual $i \in N$ (individuals veto the alternatives at the bottom of their preference).
Given $v_i \in \intvlz{m - 1}$, define $a_i = m - v_i - 1 \in \intvlz{m - 1}$ as the highest acceptable loss level for individual $i$.
For $v=(v_1,v_2)$, the rule $\PVv(\prof) = \cap_{i \in N}\set{x \in \allalts \suchthat \lprof(x)_i ≤ a_i} \cap \PE$ picks all Pareto-efficient alternatives that no individual vetoes. 
The class $\PVcl = \set{\PVv \suchthat v_1, v_2 \in \intvlz{m - 1} \text{ with } v_1 + v_2 \leq m - 1}$ is the set of those rules, and the class $\PVbcl = \set{\PVv \suchthat v_1, v_2 \in \intvlz{m - 1} \text{ with } v_1 + v_2 = m - 1} \subseteq \PVcl$ is the set of rules where the inequality is binding.

\begin{remark}
	All $\PVv$ rules differ. To see why, consider a profile $\prof$ with a preference ordering $(a_1, …, a_m)$ and the inverse preference ordering $(a_m, …, a_1)$: $\set{a_{v_2 + 1}, …, a_{m - v_1}} = \PVv(\prof) ≠ \PVv[v'](\prof) = \set{a_{v'_2 + 1}, …, a_{m - v'_1}}$.
\end{remark}

\begin{remark}
	All SCRs in $\PVcl$ are  neutral, while $\PVv \in \PVcl$ is anonymous iff $v_1 = v_2$.
\end{remark}

We define the rule $\PVe = \PVv[\left(\floor{\frac{m - 1}{2}}, \floor{\frac{m - 1}{2}}\right)]$ as the rule in $\PVcl$ that gives the highest equal veto power to both individuals. Thus, under $PV^=$, we have $v_1=v_2= \floor{\frac{m - 1}{2}}$, implying $v_1=v_2=\frac{m-1}{2}$ when $m$ is odd and $v_1=v_2= \frac{m}{2}-1$ when $m$ is even. Note that $PV^=\in\PVbcl$ iff $m$ is odd. The rule $PV^=$ is of special interest regarding its relation to $\FB$, $\VR$ and $\SL$ as well as to the minimal Rawlsian principle that will be introduced in the next section. 

\begin{theorem}\label{th:intersection}
For each $\prof \in \allprofs$, $\PVe(\prof)=H(\prof)\cap PE(\prof)$.
\end{theorem}
\begin{proof}
At every $\prof$, $\PVe$ selects all Pareto efficient alternatives that are not among the worst $\floor{\frac{m - 1}{2}}$ alternatives for every individual, in other words, those that are among the best $\ceil{\frac{m - 1}{2}} + 1 = \khalf + 1$ ones. This is equivalent to say that $\PVe$ selects every Pareto efficient alternative $x$ with $\lprof(x) ≤ (\khalf, \khalf)$. Yet, this is precisely $H(\prof)\cap PE(\prof)$, as desired.
\end{proof}

The next proposition shows that each of $\FB$, $\VR$ and $\SL$, as well as their union is a strict sub-correspondence of $\PVe$.
\begin{proposition}
  \label{th:subcorr}
   	$\FB \cup \VR \cup \SL \subsetneq \PVe$.
\end{proposition}
\begin{proof} 
	\Cref{th:intersection}, together with \cref{th:FBH,th:VRSLH}, establishes that $\FB, \VR, \SL \subseteq \PVe$. To see the strictness of the inclusion, consider the profile $\prof = (\pref_1, \pref_2)$ defined as
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} lllll|llll}
			\pref_1&a&b&c&d&e&f&g&h&i\\
			\pref_2&e&c&d&b&a&f&g&h&i\\
		\end{array}
	\end{equation}
	where $\FB(\prof) = \set{c}$, $\VR(\prof) = \set{c}$, $\SL(\prof) = \set{a, e}$ but $\PVe(\prof) = \set{a, b, c, e}$. 
 \end{proof}

\section{The minimal Rawlsian principle}
\label{sec:minprinc}
This section focuses on the notion of Rawlsianism, which aims at maximizing the welfare of the worst-off individual.
\begin{definition}[$k$-Rawlsianism] 
	\label{def:kr}
	Given $k \in \intvlz{m - 1}$, a SCR is $k$-Rawlsian iff it selects among alternatives whose losses are within $\intvlz{k}$ for both individuals, whenever such alternatives exist. 
	Formally, $\forall \prof \in \allprofs,  x, y \in \allalts$:
	$\max \lprof(x) ≤ k < \max \lprof(y) ⇒ y \notin f(\prof)$.
\end{definition}

$k$-Rawlsianism is binding at exactly those profiles where there is an alternative $x$ whose loss vector is in $\intvlz{k}^N$ (equivalently, satisfies $\max \lprof(x) ≤ k$), and is void at the other profiles. It is thus natural to wonder which values of $k$ make the constraint binding at every profile, so as to guarantee a minimal possible loss to every individual  whatever the profile.

It follows from \cref{th:BKkhalf} that $k$-Rawlsianism is binding at every profile if and only if $k$ is at least “half”.
Thus, the strongest version of $k$-Rawlsianism that is binding at every profile is when $k$ equals $\khalf$.%
\footnote{
  \label{ft:variant}
	A variant of $k$-Rawlsianism that may come to mind is to mandate that the rule be $k$-strict-Rawlsian iff it selects its winners among those alternatives whose losses are within $\intvlz{k}$ for both individuals.
	Formally:
	$\forall \prof \in \allprofs,  f(\prof) \subseteq \lprofinv(\intvlz{k}^N)$.
	(We actually thought about that version first. We thank Miguel Ballester for the improved version.)
	By the reasoning above, $k$-Rawlsianism is equivalent to $k$-strict-Rawlsianism for all $k \geq \khalf$, whereas for $k < \khalf$, no rule satisfies $k$-strict-Rawlsianism.
} 
On the other hand, this choice of $k$ reflects a general bound that makes $k$-Rawlsianism systematically constraining while there are several profiles where the minimal loss is lower than $k$.
Thus, we qualify $\khalf$-Rawlsianism as “minimal Rawlsianism”, which we formally define as follows.
\begin{definition}[Minimal Rawlsianism, \MRprop] 
	A SCR $f$ satisfies \MRprop{} iff 
	$\forall \prof \in \allprofs,  f(\prof) \subseteq H(\prof)$.
\end{definition}
Considering two SCRs $f$ and $f'$, let $f \cup f'$ denote the rule $(f \cup f')(\prof) = f(\prof) \cup f'(\prof)$. 
Given any non empty class of SCRs $F$, let $\bigcup F$ denote the maximal (least resolute) SCR that can be formed by unions of rules of $F$.

\begin{theorem}
	\label{th:equal}
	$\bigcup(\PEcl \cap \MRcl) = \PVe$.
\end{theorem}
\begin{proof}
	Observe that at each profile, $\bigcup(\PEcl \cap \MRcl)$ picks all Pareto alternatives, and only those, that are in the first half of both individuals’ preferences. This observation combined with \cref{th:intersection} establishes the result.
\end{proof}
Theorem \ref{th:equal} admits the corollary below.
\begin{corollary}\label{th:subPVe}
	A SCR $f \in \PEcl \cap \MRcl$ if and only if $f \subseteq \PVe$.
\end{corollary}

Corollary 1 and Theorem 1 lead to the following corollary: 
	
\begin{corollary}
    
	\label{th:inFH}
	$\FB, \VR, \SL \in \PEcl \cap \MRcl$. 
\end{corollary}

   
We now discuss the relationship of the class $\PVcl$ to the \MRprop{} property. The following result determines which rules in $\PVcl$ satisfy MR.

\begin{theorem}
	\label{th:pvmr}
	Among the class $\PVcl$, when $m$ is odd, only the rule $PV^=$ satisfies MR, and when $m$ is even, only the three rules $\set{\PVe, \PVv[(\frac{m}{2}, \frac{m}{2} - 1)], \PVv[(\frac{m}{2} - 1, \frac{m}{2})]}$ satisfy it.
\end{theorem}
 \begin{proof}
	Note that $[\forall i: v_i ≥ \floor{\frac{m - 1}{2}} \land \sum_i v_i ≤ m - 1]$ 
is equivalent to 
$[\exists i \suchthat v_i = \floor{\frac{m - 1}{2}} \land \floor{\frac{m - 1}{2}} ≤ v_{\ibar} ≤ \khalfAlt = \khalf]$. Thus, the claim is equivalent to the claim $\PVcl ∩ \MRcl = \set{\PVv \in \PVcl \suchthat \forall i: v_i ≥ \floor{\frac{m - 1}{2}}}$, which we now prove.

	To show the “if” part, note that the condition $\forall i: v_i ≥ \floor{\frac{m - 1}{2}}$ suffices to guarantee that  $\PVv(\prof) \subseteq H(\prof)$ for any profile . 

	To see the “only if” part, consider an arbitrary ordering $\prefi[1]$ over $\allalts$, let $\prefiinv[1]$ denote its inverse, and consider the profile $\prof = (\pref_1, \pref_2)$ where ${\pref_2} = {\prefiinv[1]}$.
	Observe that $\PVv(\prof)$ will exclusively pick winners in the first half of individual $i$ only if $v_i ≥ \floor{\frac{m - 1}{2}}$.
\end{proof} 

\section{The equal loss principle}
\label{sec:eqprinc}

This section introduces the second fairness criteria of this work, based on the idea of equal sacrifice by both players or equal loss.

Given $\prof \in \allprofs$, define $S(\prof) = \set{x \in \allalts \suchthat \lprof(x)_1 = \lprof(x)_2}$ as the alternatives ranked at the same position by both individuals.

\begin{definition}[Equal loss compatibility, ELC]
	$\forall \prof \in \allprofs: [S(\prof) ≠ \emptyset] ⇒ f(\prof) \cap S(\prof) ≠ \emptyset$.
\end{definition}
Equal loss compatibility is logically incompatible with Pareto efficiency, as formally stated by the next proposition. 
\begin{proposition}
	$\forall m ≥ 3: \PEcl ∩ \ELCcl = \emptyset$.
\end{proposition}
\begin{proof}
	Consider the profile $\prof = (\pref_1, \pref_2)$ defined as
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} lll ll}
			\pref_1&a_1&a_2 &a_3 & \ldots &a_m \\
			\pref_2&a_2& a_1 &a_3&\ldots&a_m \\
		\end{array}.
	\end{equation}
  Observe that $a_1$ and $a_2$ are the only Pareto efficient alternatives.
  Thus, all the alternatives that are ranked at the same position by both individuals, namely $\allalts \setminus \set{a_1, a_2}$, are Pareto dominated.
\end{proof}
Thus, Pareto efficiency is a fortiori incompatible with the following stronger version of equal loss compatibility.

\begin{definition}[Equal loss]
	$\forall \prof \in \allprofs: [S(\prof) ≠ \emptyset] ⇒ f(\prof) \subseteq S(\prof)$.
\end{definition}

We now embed Pareto efficiency into the equal loss requirement by mandating $f$ to pick the (unique) Pareto efficient alternative that is ranked equally by both individuals, if any.

\begin{definition}[Paretian equal loss compatibility (PEL-compatibility)]
	$\forall \prof \in \allprofs: [S(\prof) \cap \PE ≠ \emptyset] ⇒ f(\prof) \cap S(\prof) \cap \PE ≠ \emptyset$.
\end{definition}

\begin{proposition}
	$\VR$ and $\SL$ are not PEL-compatible.
\end{proposition}
\begin{proof}
	Consider the profile $\prof = (\pref_1, \pref_2)$ stated in \eqref{eq:distinct}, where $\VR(\prof) = \set{b}$ and $\SL(\prof) = \set{a, g}$:
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} llll lll | llll ll}
			\pref_1&a&b&c&d&e&f&g&h&i&j&k&l&m\\
			\pref_2&g&h&i&d&b&j&a&c&e&f&k&l&m\\
		\end{array}.
	\end{equation}
	PEL-compatibility requires to choose $d$.
\end{proof}

The following result will be useful throughout.
\begin{lemma}
	\label{th:sumlosses} 
	For any $\prof$, if $x \in \PE$ then $\lprof(x)_1+\lprof(x)_2 \leq m-1$.
\end{lemma}
\begin{proof}
Since $x \in \PE$, $\{y\in \mathcal{A}\mid y \succ_1 x\}\cap \{y\in \mathcal{A}\mid y \succ_2 x\} =  \emptyset$, which implies $\#\{y\in \mathcal{A}\mid y \succ_1 x\}+\#\{y\in \mathcal{A}\mid y \succ_2 x\} \leq m - 1$.
\end{proof}

Some rules from the class $\PVcl$ are PEL-compatible, $\PVe$ being among those.
\begin{proposition}
	\label{th:pel}	
	For any $m ≥ 3$, a rule $\PVv[(v_1, v_2)] \in \PVcl$ is PEL-compatible iff its veto levels are both at most $\floor{\frac{m}{2}}$, thus, iff $\max_{i \in \set{1, 2}} v_i ≤ \frac{m}{2}$.
\end{proposition}
\begin{proof}
	For all $\prof \in \allprofs$, if $x \in S(\prof) \cap \PE$, then $x$ is not among the last $\floor{\frac{m}{2}}$ ranks, as follows from \cref{th:sumlosses}.
	A PV rule with veto parameters at most $\floor{\frac{m}{2}}$ will thus pick all such alternatives $S(\prof) \cap \PE$, as required by PEL-compatibility.
	
	For the other direction, observe that there exists $\prof \in \allprofs$ such that for some $x \in \allalts$, $x \in S(\prof) \cap \PE$ and $x$ is positioned just better than the last $\floor{\frac{m}{2}}$ ranks (thus $\exists \prof \in \allprofs, x \in \allalts \suchthat \forall i \in \set{1, 2}: \lprof(x)_i = \floor{\frac{m - 1}{2}}$, leaving $\khalf = \floor{\frac{m}{2}}$ positions behind $x$).
	A PV rule such that $\max_{i \in \set{1, 2}} v_i > \floor{\frac{m}{2}}$ will thus not include $x$ in the set of winners, hence, the rule will fail PEL-compatibility.
\end{proof}

\Cref{th:pel} leads to the following corollary for the binding Pareto-and-veto rules.

\begin{corollary}
	\label{th:pvbpel}
	For any $m ≥ 3$, a rule $\PVv[(v_1, v_2)] \in \PVbcl$ is PEL-compatible iff $v_i = \floor{\frac{m - 1}{2}}$ and $v_{\ibar} = \khalf$ for any $\set{i, \ibar} = \set{1, 2}$.
\end{corollary}

The rules that fail PEL-compatibility will a fortiori fail the following stronger version of the Paretian equal loss property which requires that the Pareto efficient alternative ranked at the same position by both individuals, if it exists, be the unique outcome.

\begin{definition}[Paretian equal loss (PEL)]
	$\forall \prof \in \allprofs: [S(\prof) \cap \PE ≠ \emptyset] ⇒ f(\prof) = S(\prof) \cap \PE$.
\end{definition}
Thus, $\VR$, $\SL$ and those rules in $\PVcl$ that are not PEL-compatible all fail PEL. Furthermore, as we state and show below, even the rules in $\PVcl$ that are PEL-compatible fail PEL.
\begin{proposition}
	\label{th:PVnotSPEL}
	When $m ≥ 4$, all rules in $\PVcl$ fail PEL.
\end{proposition}
\begin{proof}
	Let $\allalts = \set{a, b, c, a_4, a_5, …}$.
	Consider the profile $\prof = (\pref_1, \pref_2)$ defined as
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} *6{l}}
			\pref_1&a&b&c&a_4&a_5&…\\
			\pref_2&c&b&a&a_4&a_5&…\\
		\end{array}.
	\end{equation}
	PEL requires to pick solely $b$.
	To have $f \in \PVcl$ and $f(\prof) = \set{b}$ requires that $v_1 ≥ m - 2$ (for $c \notin f(\prof)$) and $v_2 ≥ m - 2$ (for $a \notin f(\prof)$), which implies $2m - 4 ≤ \sum v_i$. Also, the definition of $\PVcl$ requires that $\sum v_i ≤ m - 1$. However, $2m - 4 ≤ m - 1$ is satisfied only when $m ≤ 3$.
\end{proof}

\begin{remark}
When $m = 3$, $\PVv[(1, 1)]$ satisfies PEL.
\end{remark}

\begin{proposition}
	$\FB$ satisfies PEL.
\end{proposition}
\begin{proof}
	Pick any profile $\prof$ and any $x \in PE(\prof)$ with $\lprof(x) = (k, k)$ for some $k \in \intvlz{m - 1}$. Let us show that $\FB(\prof) = \set{x}$. Consider any $y \in \FB(\prof)$. As $\FB$ minimizes the maximal loss, $\max \lprof(y) ≤ \max \lprof(x) = k$. Since $x \in PE(\prof)$, we have $\max \lprof(y) ≥ k$ (otherwise $\min \lprof(y) ≤ \max \lprof(y) < k$ and $y$ Pareto-dominates $x$). Hence, $\max \lprof(y) = k$, thus $x = y$.
\end{proof}

PEL, failed by all rules we consider but one, allows to distinguish $\FB$ from the rest. Moreover, by satisfying both conditions, $\FB$ establishes the compatibility between PEL and MR. However, as discussed below, this compatibility vanishes when another stronger version of PEL-compatibility is adopted. 

Call the dispersion of a loss vector $l$ at $\prof$ the value $d(l) = \abs{l_1 - l_2}$. 
Thus, $(d \circ \lprof)(x) = \max\lprof(x) - \min\lprof(x)$.
We show in \cref{sec:spreads} that $d$ coincides with several commonly used spread measures.

Given a profile $\prof \in \allprofs$, define $\min_{\PE} (d \circ \lprof)$ as the minimal dispersion obtained by loss vectors of Pareto efficient alternatives in that profile, and $\argmin_{\PE} (d \circ \lprof)$ as the Pareto efficient alternatives whose loss vectors have minimal dispersion among Pareto efficient alternatives.

Define the minimal dispersion (MD) condition as follows.
\begin{definition}[Minimal dispersion]
	$f(\prof) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset$, $\forall \prof \in \allprofs$.
\end{definition}
MD requires the outcome to contain some Pareto efficient alternatives whose loss vectors have minimal dispersion. As such, MD is another strengthening of PEL-compatibility while it is logically independent of PEL. Nevertheless, although there are rules that satisfy both PEL and MR, MD turns out to be logically incompatible with MR (except for sufficiently low values of $m$).

\begin{theorem}
	\label{th:noMRMD}
	$[\MRcl \cap \MDcl \neq \emptyset] ⇔ [m ≤ 6 \lor m = 8]$.
\end{theorem}
\begin{proof}
	We prove the theorem through Lemmas 2 to 5. 

\Cref{th:PNonEmpty} states that a Pareto efficient alternative that minimizes dispersion among the top $\ceil{\frac{2m - 4}{3}}$ of both individuals always exists.

\begin{lemma}
	\label{th:PNonEmpty}
	Given $m ≥ 3$,$\forall \prof: \lprofinv(\intvlz{\ceil{\frac{2m - 4}{3}}} × \intvlz{\ceil{\frac{2m - 4}{3}}}) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset$.
\end{lemma}
\begin{proof}
	Consider any $x \in \argmin_{\PE} (d \circ \lprof)$ and let $i$ denote any individual such that $\max \lprof(x) = \lprof(x)_i$. In the sake of brevity, define $t = \ceil{\frac{2m - 4}{3}}$.
	
	If $\lprof(x)_i ≤ t$ then $\lprof(x)_{\ibar} ≤ t$ so that $x \in \lprofinv(\intvlz{t} × \intvlz{t}) \cap \argmin_{\PE} (d \circ \lprof)$, proving the claim. 

	If $\lprof(x)_i > t$, let $A = \set{a \suchthat \lprof(a)_i ≤ t}$ be the $t + 1$ top alternatives for $i$. 
	Define $y = \argmin_A \lprof(.)_{\ibar}$ as the best alternative for $\ibar$ in $A$. Observe that $y \in \PE$: for $i$, only the alternatives in $A$ can be preferred to $y$, and those are less preferred than $y$ for $\ibar$.
	
	Since $\lprof(x)_i > t$ and $y \in A$, we see that $\lprof(y)_i<  \lprof(x)_i$.
	It follows that $\lprof(x)_{\ibar}<\lprof(y)_{\ibar}  $ to avoid that $y$ Pareto-dominates $x$. Moreover, if $\lprof(y)_{\ibar} \leq \lprof(y)_i $, then \[\lprof(x)_{\ibar} < \lprof(y)_{\ibar} ≤ \lprof(y)_i < \lprof(x)_i\] which implies that $d(\lprof(y)) < d(\lprof(x))$, contradicting $x \in \argmin_{\PE} (d \circ \lprof)$. Thus, we have $\lprof(y)_i < \lprof(y)_{\ibar}$.

	Observe that $2(m - t - 1) ≤ t + 2$.
	Indeed, $\frac{2m - 4}{3} ≤ t = \ceil{\frac{2m - 4}{3}}$, thus $2m - 4 ≤ 3t$.
	 
	Also,  when $m ≥ 3$, $m - t - 1 ≤ t$.
	Indeed, define $\epsilon = t - \frac{2m - 4}{3}$, then $m - 1 ≤ 2t$ iff $3m - 3 ≤ 6(ε + \frac{2m - 4}{3})$ iff $5 ≤ m + 6 ε$ which holds as when $m = 3$, $ε = 1/3$ and when $m = 4$, $ε = 2/3$.
	
	By construction, $\forall a ≠ y \in A: \lprof(y)_{\ibar} < \lprof(a)_{\ibar}$, hence, $\lprof(y)_{\ibar} ≤ m - 1 - \card{(A \setminus \set{y})} = m - t - 1$.
	We obtain that $\lprof(y)_i < \lprof(y)_{\ibar}≤ m - t - 1 ≤ t$, which yields that $y \in \lprofinv(\intvlz{t} × \intvlz{t})$ and that $d(\lprof(y)) ≤ m - t - 1$. 
	
	We also have that $m - t - 1 ≤ d(\lprof(x))$:
	from $2(m - t - 1) ≤ t + 2$, $m - t - 1 ≤ t + 2 - (m - t - 1) = 2(t + 1) - m + 1 ≤ 2 \lprof(x)_i - m + 1 = 2 \max \lprof(x) - m + 1$; 
	and by \cref{th:sumlosses}, 
	$\max \lprof(x) ≤ m - 1 - \min \lprof(x)$, whence 
	$2 \max \lprof(x) - m + 1 ≤ \max \lprof(x) - m + 1 + m - 1 - \min \lprof(x) = d(\lprof(x))$.
	
	To conclude, note that $d(\lprof(y)) ≤ m - t - 1 ≤ d(\lprof(x))$ implies that $y \in \argmin_{\PE} (d \circ \lprof)$.
\end{proof}

\Cref{th:PEmpty} shows the existence of some profile where there is a Pareto efficient and dispersion minimizing alternative among the top $t$ alternatives of one of the individuals, as long as $t<\frac{2m-4}{3}$.
\begin{lemma}
	\label{th:PEmpty}
	For any $t \in \N$ with $t < \frac{2m - 4}{3}$, we have the following two implications:
	\begin{itemize}
		\item $\exists \prof \suchthat \lprofinv(\intvlz{t} × \intvlz{m - 1}) \cap \argmin_{\PE} (d \circ \lprof) = \emptyset$;
		\item $\exists \prof \suchthat \lprofinv(\intvlz{m - 1} × \intvlz{t}) \cap \argmin_{\PE} (d \circ \lprof) = \emptyset$.
	\end{itemize}
\end{lemma}
\begin{proof}
	We prove only the first implication: the other one admits a similar proof by swapping the roles of individuals 1 and 2.
	
	Note that $\forall k \in \N$, $k < \frac{2m - 4}{3} ⇔ k ≤ \ceil{\frac{2m - 7}{3}}$: if $\frac{2m - 4}{3} \in \N$, $k < \frac{2m - 4}{3} = \ceil{\frac{2m - 4}{3}} ⇔ k ≤ \ceil{\frac{2m - 4}{3}} - 1$; and otherwise, for some $0 < ε < 1$, $k < \frac{2m - 4}{3} = \ceil{\frac{2m - 4}{3}} - ε ⇔ k ≤ \ceil{\frac{2m - 4}{3}} - 1$.
%	Thus, suffices to show that for some $t' ≥ \ceil{\frac{2m - 7}{3}}, \exists \prof \suchthat \lprofinv(\intvlz{t'} × \intvlz{m - 1}) \cap \argmin_{\PE} (d \circ \lprof) = \emptyset$. 

	When $2 ≤ m ≤ 3$, the claim holds because $\intvlz{\ceil{\frac{2m - 7}{3}}} × \intvlz{m - 1} = \emptyset$.
	
	Defining $t' = \max \set{\khalf, \ceil{\frac{2m - 7}{3}}}$ and considering $4 ≤ m$,
	we will define a profile $\prof$ such that $\lprofinv(\intvlz{t'} × \intvlz{m - 1}) \cap \argmin_{\PE} (d \circ \lprof) = \emptyset$.
	This proves the claim as, with $t < \frac{2m - 4}{3}$ (thus $t ≤ \ceil{\frac{2m - 7}{3}}$), $\intvlz{t} × \intvlz{m - 1} \subseteq \intvlz{t'} × \intvlz{m - 1}$.
	
 	Observe that $\ceil{\frac{2m - 7}{3}} < \frac{2m - 4}{3} ≤ m - 2$ (the latter inequality being equivalent to $2 ≤ m$) and $\khalf ≤ \frac{m}{2} ≤ m - 2$ (the latter inequality being equivalent to $4 ≤ m$). Thus, $0 ≤ m - t' - 2$.

	Observe that $m = t' + 1 + (m - t' - 2) + 1$.
	We label the alternatives as $\set{a_1, …, a_{t' + 1}, c_1, …, c_{m - t' - 2}, x}$ and consider the sequences $A = (a_1, …, a_{t' + 1})$ and $C = (c_1, …, c_{m - t' - 2})$. Define $\prof$ as associating to individual $1$ (resp. individual 2) the preference order $(A, x, C)$ (resp. $(C, x, A)$).

	Observe that as $\lprof(x)_1 = t' + 1$, $x \notin \lprofinv(\intvlz{t'} × \intvlz{m - 1})$, and $x \in \PE$, so the claim is proved by showing that $\forall y \in A \cup C: d(\lprof(y)) > d(\lprof(x))$, so that $\forall y \in A \cup C: y \notin \argmin_{\PE} (d \circ \lprof)$.
	
	Note that $\card{A} - \card{C} ≥ 0$ as $\card{A} - \card{C} = t' + 1 - (m - t' - 2) = 2t' + 3 - m ≥ 2\khalf + 3 - m ≥ 2 \frac{m - 1}{2} + 3 - m = 2$ where we rely on the equality $\floor{\frac{m}{2}}=\ceil{\frac{m-1}{2}}$ which holds for any integer $m$.
	
	Thus, $d(\lprof(x)) = \card{A} - \card{C} = 2t' + 3 - m$.
	
	For any $a_i \in A$, observe that $\lprof(a_i) = (i - 1, \card{C} + 1 + i - 1)$ which implies that $d(\lprof(a_i)) = m - t' - 1$. It follows that $d(\lprof(a_i)) > d(\lprof(x))$, equivalently, $m - t' - 1 > 2t' + 3 - m$, as $3t' < 2m - 4$ by hypothesis.
	
	Likewise, for any $c_i \in C$, $\lprof(c_i) = (\card{A} + 1 + (i - 1), i - 1)$ thus $d(\lprof(c_i)) = t' + 2$.
	Using $\card{A} ≥ \card{C}$, it follows that $d(\lprof(c_i)) = \card{A} + 1 ≥ \card{C} + 1 = d(\lprof(a_i)) > d(\lprof(x))$, thus $d(\lprof(c_i)) > d(\lprof(x))$.
\end{proof}

The next lemma states that to ensure the existence of an alternative within the first $t$ alternatives for both players that minimizes dispersion among the Pareto efficient ones, it is necessary and sufficient to set $t$ at least $\frac{2m - 4}{3}$. This follows from \cref{th:PNonEmpty,th:PEmpty}.
\begin{lemma}
	\label{th:caractEmpty}
	Given $m ≥ 3$, $\forall t \in \intvlz{m - 1}$, the following two statements are logically equivalent: 
	\begin{enumerate}
		\item \label{it:tbound} $t ≥ \frac{2m - 4}{3}$,
		\item \label{it:Pt} $\forall \prof: \lprofinv(\intvlz{t} × \intvlz{t}) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset$.
	\end{enumerate}
\end{lemma}

\Cref{th:caractEmpty} in turn permits to characterize the number of alternatives in which a Pareto efficient alternative minimizing dispersion is guaranteed to be found in the first half, as stated by \cref{th:profsIncompat}.

\begin{lemma}
	\label{th:profsIncompat}
	$\forall \prof: H(\prof) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset ⇔ m ≤ 6 \lor m = 8$
\end{lemma}
\begin{proof}
	When $m = 2$, $H(\prof) = \lprofinv(\intvlz{1} × \intvlz{1}) = \prof$ thus $H(\prof) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset$.
	
	When $m ≥ 3$, fix $t = \khalf$ and use \cref{th:caractEmpty} to obtain:
	\begin{equation}
		m ≤ \frac{3 \khalf + 4}{2} ⇔ \forall \prof: H(\prof) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset.
	\end{equation}
	The left hand side is equivalent, when $m$ is odd, to $m ≤ \frac{3m + 5}{4}$ thus $m ≤ 5$, in other words, $m \in \set{3, 5}$, and when $m$ is even, to $m ≤ \frac{3m + 8}{4}$ thus $m ≤ 8$, that is, $m \in \set{4, 6, 8}$.
\end{proof}

It follows from \cref{th:profsIncompat} that when $m ≤ 6$ or $m = 8$, the SCR $H(\prof) \cap \argmin_{\PE} (d \circ \lprof)$ is well-defined and satisfies MR and MD by construction; and when $m = 7$ or $m ≥ 9$, there is no $f \in \MRcl$ that satisfies MD.
\end{proof}

\begin{remark}
  It follows from \cref{th:caractEmpty} that for $m ≥ 3$, $k$-Rawlsianism (\cref{def:kr}) and MD are compatible for $k \geq \frac{2m - 4}{3}$ and incompatible for $k < \frac{2m - 4}{3}$.
  \footnote{Similarly, $k$-strict-Rawlsianism (\cref{ft:variant}) and MD are compatible for $k \geq \frac{2m - 4}{3}$ and incompatible for $k ≤ \frac{2m - 4}{3}$.}
  We thank an anonymous reviewer for a question that lead to this observation.
  \commentOC{Dear colleagues, please check this remark and the footnote (both new).}
\end{remark}

The minimal Rawlsian and minimal dispersion principles being logically incompatible, the SCRs that satisfy MR (namely $\FB$, $\VR$, $\SL$ and the rules in $\PVcl$ identified by \cref{th:pvmr}) all fail MD. 

\begin{remark}
	As $\FB$ has a strong egalitarian flavor, it may be surprising that it fails $\MD$. The following profile $\prof = (\pref_1, \pref_2)$ (built using the proof of \cref{th:caractEmpty}) illustrates this failure for $m = 7$.
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} *7{l}}
			\pref_1&y& a_1 & a_2 & a_3 & x & c_1 & c_2\\
			\pref_2&c_1& c_2 & x & y & a_1 & a_2 & a_3\\
		\end{array}.
	\end{equation}
	Observe that $\FB(\prof) = \set{y}$ while the $\MD$ principle mandates $x$ to be picked.
\end{remark}

Since \cref{th:pvmr} shows that most rules in $\PVcl$ fail MR, the following result determines the subclass of $\PVcl$ satisfying MD. 

\begin{proposition}
	\label{th:pvMD}
	For $m ≥ 3$, $\PVv[(v_1, v_2)]$ satisfies MD iff $\max_{i \in \set{1, 2}} v_i ≤ \frac{m + 1}{3}$.
\end{proposition}
\begin{proof}
	Define $t = \min_{i \in \set{1, 2}} (m - 1 - v_i) \in \N$.
	Observe that $\max_{i \in \set{1, 2}} v_i ≤ \frac{m + 1}{3} ⇔ \forall i \in \set{1, 2}: v_i ≤ \frac{m + 1}{3} ⇔ \forall i \in \set{1, 2}: m - 1 - v_i ≥ \frac{2m - 4}{3} ⇔ t ≥ \frac{2m - 4}{3}$.
	
	If $t = m - 1 - v_1$, define $S = \intvlz{t} × \intvlz{m - 1}$, otherwise (implying that $t = m - 1 - v_2$), define $S = \intvlz{m - 1} × \intvlz{t}$.
	By definition, $\forall \prof: \PVv[(v_1, v_2)](\prof) = \lprofinv(\intvlz{m - 1 - v_1} × \intvlz{m - 1 - v_2}) \cap \PE$.
	It follows that $\forall \prof$:
	\begin{equation}
		\lprofinv(\intvlz{t} × \intvlz{t}) \cap \PE \subseteq \PVv[(v_1, v_2)](\prof)
	\end{equation} 
	and
	\begin{equation}
		\PVv[(v_1, v_2)](\prof) \subseteq \lprofinv(S) \cap \PE,
	\end{equation}
	therefore (intersecting all sets with $\argmin_{\PE} (d \circ \lprof)$ and using $\PE \cap \argmin_{\PE} (d \circ \lprof) = \argmin_{\PE} (d \circ \lprof)$):
	\begin{equation}
		\lprofinv(\intvlz{t} × \intvlz{t}) \cap \argmin_{\PE} (d \circ \lprof) \subseteq \PVv[(v_1, v_2)](\prof) \cap \argmin_{\PE} (d \circ \lprof)
	\end{equation} 
	and
	\begin{equation}
		\PVv[(v_1, v_2)](\prof) \cap \argmin_{\PE} (d \circ \lprof) \subseteq \lprofinv(S) \cap \argmin_{\PE} (d \circ \lprof).
	\end{equation}
	
	It follows from \cref{th:caractEmpty,th:PEmpty} that $t ≥ \frac{2m - 4}{3} ⇔ \forall \prof: \lprofinv(\intvlz{t} × \intvlz{t}) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset ⇔ \forall \prof: \lprofinv(S) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset$, and thus $\max_{i \in \set{1, 2}} v_i ≤ \frac{m + 1}{3} ⇔ t ≥ \frac{2m - 4}{3} ⇔ \forall \prof: \PVv[(v_1, v_2)](\prof) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset$.
\end{proof}

\begin{remark}
   As MD implies PEL-compatibility, the class of PV rules that satisfy MD is a subclass of those that are PEL-compatible. This relationship can be more precisely observed by comparing \cref{th:pel} and \cref{th:pvMD}. 
\end{remark}

%We now further analyze the relationship between the minimal dispersion principle and Pareto-and-veto rules, beyond the proximity suggested by \cref{th:pvMD}. 

\begin{remark}
	\Cref{th:pvMD} shows that PV rules with $\max_i v_i ≤ \frac{m + 1}{3}$ satisfy MD. On the other hand, these rules fail two stronger versions of MD, one which mandates to pick \emph{all} minimal dispersion alternatives (thus $\argmin_{\PE} (d \circ \lprof) \subseteq f(\prof)$) and the other which mandates to pick \emph{only} minimal dispersion alternatives (thus $\argmin_{\PE} (d \circ \lprof) \supseteq f(\prof)$). To illustrate this for the former, for $m = 5$, consider the rule $PV^{(2, 2)}$ and the profile $\prof = (\pref_1, \pref_2)$ defined as
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} *5{l}}
			\pref_1&a& b & c & d & e \\
			\pref_2&c& d & e & b & a\\
		\end{array}.
	\end{equation}
	Here, $\argmin_{\PE} (d \circ \lprof) = \set{b, c}$ while $PV^{(2, 2)}(\prof) = \set{c}$.

For the latter, consider the profile $\prof = (\pref_1, \pref_2)$ with $m=7$ defined as
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} *7{l}}
			\pref_1&a& b & c & d & e & f & g\\
			\pref_2&g& f & e & d & c& b & a \\
		\end{array}.
	\end{equation}
Observe that $\argmin_{\PE} (d \circ \lprof) = \set{d}$ whereas $PV^{(2, 2)}(\prof)=\{c,d,e\}$.
\end{remark}

\begin{remark}
	To ensure $\argmin_{\PE} (d \circ \lprof) \subseteq f(\prof)$ and $\argmin_{\PE} (d \circ \lprof) \supseteq f(\prof)$, one can define the rule $\MD(\prof) = \argmin_{\PE}(d \circ \lprof)$ which selects all Pareto efficient alternatives that minimize the dispersion and only those. As mentioned in \cref{ft:equalarea}, this rule is the finite version of \possessivecite{thomson1994cooperative} equal area rule in our framework with no disagreement outcome.
 As the rules $\FB$, $\VR$ and $\SL$ fail the MD principle, they are distinct from the rule $\MD$. Also, the rule $\MD$ is not in $\PVcl$: $\MD$ satisfies PEL while no rule in $\PVcl$ does (for $m ≥ 4$), as shown by \cref{th:PVnotSPEL}. It follows that satisfying MD does not imply being a Pareto-and-veto rule.
\end{remark}

We end this section by showing that every profile admits some Pareto efficient alternative with a dispersion of at most $\khalf$. Moreover, there is no guarantee of finding an efficient alternative with a dispersion lower than $\khalf$. In other words, $\khalf$ is a general upper bound on dispersion.

\begin{proposition}
    \label{th:dispbound}
	$[\forall \prof, \exists x \in \PE \suchthat d(\lprof(x)) ≤ k] ⇔ k ≥ \khalf$.
\end{proposition}
\begin{proof}
    \Cref{th:intersection} establishes, $\forall \prof$, the existence of an alternative $x \in \PE \cap H(\prof)$. Thus $d(\lprof(x)) ≤ \khalf$, proving the “if” part. To show the "only if" part, consider the profile $\prof = (\pref_1, \pref_2)$ defined as
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} *8{l}}
			\pref_1&a_1& a_2 & … & a_{\khalf} & a_{\khalf + 1} & a_{\khalf + 2} & … & a_m\\
			\pref_2&a_{\khalf + 1}& a_{\khalf + 2} & … & a_m & a_1& a_2 & … & a_{\khalf} \\
		\end{array}
	\end{equation}
   where only $a_1$ and $a_{\khalf + 1}$ are Pareto efficient. Their dispersion is $\khalf$. Thus, one cannot ensure the existence of an efficient alternative with $k < \khalf$.
\end{proof}

\begin{remark}
    Given that there is an upper bound on dispersion, one can define the following condition.
    An SCR $f$ satisfies $k$-bounded dispersion iff $\forall \prof \in \allprofs, \forall x \in f(\prof), d(\lprof(x)) ≤ k$. The condition gets weaker with increasing $k$. Moreover, by \cref{th:dispbound}, it is satisfiable if and only if $k ≥ \khalf$. Therefore, its strongest satisfiable version is $\khalf$-bounded dispersion, which is implied by MR.
\end{remark}

\section{Reconciling the two principles}
\label{sec:reconc}
Given the incompatibility between MR and MD, one can attempt to reconcile the two principles by imposing minimal dispersion over the alternatives that are minimally Rawlsian. 

Given a profile, let us call “Rawlsian minimal dispersion (RMD) alternatives” those that minimize dispersion among the Pareto efficient alternatives within the first half. As every profile admits RMD alternatives, we can define the RMD principle as the requirement that the social choice always contains an RMD alternative while remaining within the first half.
\begin{definition}[Rawlsian minimal dispersion, RMD]
	$\forall \prof \in \allprofs$:
	$f(\prof) \subseteq H(\prof)$
	and 
	$f(\prof) \cap \argmin_{H(\prof) \cap \PE} (d \circ \lprof) ≠ \emptyset$.
\end{definition}

RMD strengthens MR. On the other hand, the relationship between RMD and MD depends on $m$: when $m$ is small, RMD is stronger than MD while when $m$ is large, no rule can satisfy both RMD and MD (because there are profiles where all Pareto efficient dispersion minimizers are out of the first half, by \cref{th:profsIncompat}).
Summarizing, when $m$ is small enough ($m ≤ 6$ or $m = 8$), and only then, first, RMD implies MD, and second, some rules are both RMD and MD.
\begin{proposition}
	\label{th:RMDMD}
	$[m ≤ 6 \lor m = 8] ⇔ \RMDcl \subseteq \MDcl ⇔ \RMDcl \cap \MDcl ≠ \emptyset$.
\end{proposition}
\begin{proof}
	First consider $[m ≤ 6 \lor m = 8] ⇒ \RMDcl \subseteq \MDcl$. \Cref{th:profsIncompat} indicates that $\forall \prof: H(\prof) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset ⇔ m ≤ 6 \lor m = 8$. 
	And $[H(\prof) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset] ⇒ [\argmin_{H(\prof) \cap \PE} (d \circ \lprof) \subseteq \argmin_{\PE} (d \circ \lprof)]$.
	Given $f \in \RMDcl$, $f(\prof) \cap \argmin_{H(\prof) \cap \PE} (d \circ \lprof) ≠ \emptyset$, thus, when $m ≤ 6 \lor m = 8$, $f(\prof) \cap \argmin_{\PE} (d \circ \lprof) ≠ \emptyset$.
	
	Second, observe that $\RMDcl \subseteq \MDcl ⇒ \RMDcl \cap \MDcl ≠ \emptyset$.
	
	To conclude, we prove that $\RMDcl \cap \MDcl ≠ \emptyset ⇒ [m ≤ 6 \lor m = 8]$.
	As $\RMDcl \subseteq \MRcl$, we have $[\RMDcl \cap \MDcl ≠ \emptyset] ⇒ [\MRcl \cap \MDcl ≠ \emptyset]$. And from \cref{th:noMRMD}, the latter implies $[m ≤ 6 \lor m = 8]$.
\end{proof}
	
\begin{theorem}
	\label{th:compatRMD}
	 $\FB$, $\VR$, $\SL$ fail RMD, and $\PVcl \cap \RMDcl = \set{\PVe}$.
\end{theorem}
\begin{proof}
	Consider the profile $\prof = (\pref_1, \pref_2)$ with 11 alternatives, $\set{a, b, c, d, e, f, g, h,\allowbreak w, x, y}$, such that (the bar indicates the “half” position)
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} *6{l}|ll}
			\pref_1&x&a&b&c&d&y&w&\ldots \\
			\pref_2&e&f&g&y&x&h&w&\ldots
		\end{array}.
	\end{equation}

$H(\prof)=\{x, y\}$ which are both Pareto efficient. For a SCR $f$ to satisfy RMD, we must have $y \in f(\prof)$. As $\FB(\prof) = \VR(\prof)=\{x\}$, both rules fail RMD. 

To see that $\SL$ fails RMD, consider the following profile $\prof$ with $\SL(\prof)=\set{a, c}$ while RMD requires $b \in \SL(\prof)$. 

	\begin{equation}
		\begin{array}{l @{:\hskip 2em} lll|ll}
			\pref_1&a&b&c&d&e \\
			\pref_2&c&b&a&d&e
		\end{array}.
	\end{equation}

We now turn to the rules in $\PVcl$. As RMD implies MR, $\PVcl ∩ \RMDcl \subseteq \PVcl ∩ \MRcl$, and by \cref{th:pvmr}, $\PVcl ∩ \MRcl = \set{\PVe}$ when $m$ is odd and $\PVcl ∩ \MRcl = \set{\PVe, \PVv[(\frac{m}{2}, \frac{m}{2} - 1)], \PVv[(\frac{m}{2} - 1, \frac{m}{2})]}$ when $m$ is even.
Thus, we need only prove that for $m$ even, $\PVv[(\frac{m}{2}, \frac{m}{2} - 1)]$ and $\PVv[(\frac{m}{2} - 1, \frac{m}{2})]$ fail RMD. To see this, consider the profile $\prof = (\pref_1, \pref_2)$ defined as
	\begin{equation}
		\begin{array}{l @{:\hskip 2em} llll}
			\pref_1&a&b&c&d \\
			\pref_2&d&c&a&b
		\end{array}
	\end{equation}
where $\PVv[(\frac{m}{2}, \frac{m}{2} - 1)](\prof)=\{a\}$ while RMD requires $c \in \PVv[(\frac{m}{2}, \frac{m}{2} - 1)](\prof)$. A similar argument shows that $\PVv[(\frac{m}{2} - 1, \frac{m}{2})]$ fails RMD.

By \cref{th:equal}, $\PVe(\prof) = H(\prof) \cap \PE$, thus, it satisfies RMD.
\end{proof}

$\PVe$ satisfies the RMD principle at the expense of resoluteness, since it picks every Pareto efficient alternative within the first half. It is thus natural to seek for a stronger principle that imposes more resoluteness. To this end, we define the Strong RMD principle, which requires to pick only RMD alternatives.
\begin{definition}[Strong Rawlsian minimal dispersion, SRMD]
	$\forall \prof \in \allprofs:
	f(\prof) \subseteq \argmin_{H(\prof) \cap \PE} (d \circ \lprof)$.
\end{definition}

The following result is the counterpart to \cref{th:RMDMD} for SRMD.
\begin{proposition}
	$[m ≤ 6 \lor m = 8] ⇔ \SRMDcl \subseteq \MDcl ⇔ \SRMDcl \cap \MDcl ≠ \emptyset$.
\end{proposition}
\begin{proof}
	First, it follows from $[m ≤ 6 \lor m = 8] ⇒ \RMDcl \subseteq \MDcl$ (by \cref{th:RMDMD}) and $\SRMDcl \subseteq \RMDcl$ that $[m ≤ 6 \lor m = 8] ⇒ \SRMDcl \subseteq \MDcl$. 
	
	Second, observe that $\SRMDcl \subseteq \MDcl ⇒ \SRMDcl \cap \MDcl ≠ \emptyset$.
	
	To conclude, we prove that $\SRMDcl \cap \MDcl ≠ \emptyset ⇒ [m ≤ 6 \lor m = 8]$.
	As $\SRMDcl \subseteq \MRcl$, we have $[\SRMDcl \cap \MDcl ≠ \emptyset] ⇒ [\MRcl \cap \MDcl ≠ \emptyset]$. And from \cref{th:noMRMD}, the latter implies $[m ≤ 6 \lor m = 8]$.
\end{proof}
	
It also follows from \cref{th:equal} that $\PVe$ fails Strong RMD. Thus, no rule that we have examined so far satisfies Strong RMD. Now, we define the Strong RMD rule $f(\prof) = \argmin_{H(\prof) \cap \PE} (d \circ \lprof)$ for each $\prof \in \allprofs$ as the least resolute rule satisfying Strong RMD. 
The Strong RMD rule (or SRMD rule) might appear as a reasonable compromise to satisfy the two main concepts exposed here (besides Pareto), that of being minimally Rawlsian and that of favoring small dispersion alternatives. It is also reasonably resolute.
\begin{proposition}
	The SRMD rule $f$ selects at most two alternatives: $\forall \prof \in \allprofs: 1 ≤ \card{f(\prof)} ≤ 2$.
\end{proposition}
\begin{proof}
	Consider any $x \in \argmin_{H(\prof) \cap \PE} (d \circ \lprof)$, any $i \suchthat \min \lprof(x) = \lprof(x)_i$ and  any $y \in \argmin_{H(\prof) \cap \PE} (d \circ \lprof)$. We first prove that $\min \lprof(y) = \lprof(y)_i$ iff $y = x$. Equivalently, we prove that $\forall a \in H(\prof): \lprof(a)_i ≠ \lprof(x)_i ⇒ [a \notin \argmin_{H(\prof) \cap \PE} (d \circ \lprof) \lor \min \lprof(a) ≠ \lprof(a)_i]$. Indeed, consider any $a \in H(\prof) \suchthat \lprof(a)_i < \lprof(x)_i$, then $\lprof(a)_{\ibar} > \lprof(x)_{\ibar}$ (because $x \in \PE$), so $\lprof(a)_i < \lprof(x)_i ≤ \lprof(x)_{\ibar} < \lprof(a)_{\ibar}$ and $(d \circ \lprof)(a) > (d \circ \lprof)(x)$; and considering now any $a \in H(\prof) \suchthat \lprof(a)_i > \lprof(x)_i$, then $\lprof(a)_{\ibar} < \lprof(x)_{\ibar}$ is required for $a \in \PE$, and if $\min \lprof(a) = \lprof(a)_i$ then $\lprof(x)_i < \lprof(a)_i ≤ \lprof(a)_{\ibar} < \lprof(x)_{\ibar}$ and $(d \circ \lprof)(a) < (d \circ \lprof)(x)$, contradicting $x \in \argmin_{H(\prof) \cap \PE} (d \circ \lprof)$, so that again $\min \lprof(a) ≠ \lprof(a)_i$.
	
	To conclude, observe that if $\argmin_{H(\prof) \cap \PE} (d \circ \lprof)$ contain at least two elements (say, $x$ and $y$), one of them, say, $x$, has $\min \lprof(x) = \lprof(x)_i$, the other one has $\min \lprof(y) = \lprof(y)_{\ibar}$, and thus there cannot be a third element $z$ in $\argmin_{H(\prof) \cap \PE} (d \circ \lprof)$ as neither $\min \lprof(z) = \lprof(z)_i$ nor $\min \lprof(z) = \lprof(z)_{\ibar}$ is possible, by the above result.
\end{proof}

One can define a refinement of the SRMD rule through the notion of \emph{anonymous dominance} of loss vectors. 

Given two loss vectors $l, l' \in \lvs$, say that 
$l$ dominates $l'$, denoted $l ⊲ l'$, iff $\min l ≤ \min l' \land \max l ≤ \max l'$ with one of these inequalities being strict.
For any profile $\prof$, $E(\prof)$ denotes the alternatives whose loss vectors are not dominated: $E(\prof) = \set{x \in \allalts \mid \nexists y \in \allalts: \lprof(y) ⊲ \lprof(x)}$.

The rule SRMD$^*$ that selects $\argmin_{H(\prof) \cap \PE \cap E(\prof)} (d \circ \lprof)$ is then a refinement of the SRMD rule, since the anonymous dominance is used as a tie-breaker, and thus picks at most two alternatives.

Note also that this rule is equivalent, within the set of alternatives with minimal dispersion, to minimize the sum of losses (equivalently, pick the Borda preferred alternative). 
This is also equivalent to minimize the best loss and in turn equivalent to minimize the worst loss: given two losses $l, l'$ with $d(l) = d(l')$, $l$ dominates $l'$ iff $\sum l < \sum l'$ iff $\min l < \min l'$ iff $\max l < \max l'$.

\section{Concluding remarks}
\label{sec:concl}
Axiomatic analysis of social choice rules with or without strategic concerns presents two strands of the literature that complement each other. This complementarity appears less balanced in two-person collective choice problems where there is a clear focus on a strategic analysis that usually adopts subgame perfect equilibrium as the solution concept.%
\footnote{While we will not restate here the relevant papers already cited in the introduction \commentOC{Now in the review?}, we wish to remark that the focus on subgame perfect equilibrium can be explained by the classical result of \citet{HurwiczSchmeidler78} and \citet{Maskin99} on the impossibility of Nash implementing Pareto efficient two-person social choice rules.} 

\begin{table}
	\begin{tabular}{l*{5}{c}}
		\toprule
		& MR & PEL-compatible & PEL & MD & RMD\\
		\midrule
		$\FB$ & ✓ & ✓ & ✓ & ✕ & ✕\\
		$\VR$ & ✓ & ✕ & ✕ & ✕ & ✕\\
		$\SL$ & ✓ & ✕ & ✕ & ✕ & ✕\\
		\bottomrule
	\end{tabular}
	\caption{Summary of the results about $\FB$, $\VR$ and $\SL$. 
	A tick (✓) means that the SCR satisfies the corresponding property for any value of $m ≥ 4$ and $n$.}%; a cross (✕) means that the opposite holds.}
	\label{fig:propsR}
\end{table}

The richness of the non-strategic axiomatic analysis of collective choice with three or more individuals is accompanied by a wealthy list of conceived social choice rules. On the other hand, for two individuals, it is hard to name a prominent social choice rule beyond unanimity compromise, the shortlisting rule, the veto-rank rule, and the class of Pareto-and-veto rules. Moreover, these social choice rules are conceived under different interpretations of the two-person collective choice model, thus being analyzed from somewhat different perspectives.

We bring a consideration based on a common interpretation and perspective. The axiomatic analysis we propose is free of strategic concerns and relies on two basic principles that we identify: the minimally Rawlsian principle and the equal loss principle. These two principles that emerge from the existing literature exhibit an incompatibility. More precisely, no minimally Rawlsian social choice rule can ensure to pick an alternative that minimize the dispersion of the loss vector.
\Cref{fig:propsR,fig:propsCexplicit} summarize our findings.\footnote{It should be noted that the axioms listed on \Cref{fig:propsR} do not characterize the SCRs that we discuss. This is somehow expected, as these axioms impose conditions at a given profile without alluding to the consequences when the given profile is modified, i.e., they are “punctual” in the sense of \citet{thomson2012axiomatics}. We thank Sylvain Béal for this comment.}

\begin{table}
	\small
	\begin{tabular}{l*{5}{c}}
		\toprule
		& MR & PEL-comp. & PEL & MD & RMD\\
		\midrule
		$\PVcl$ & $\min v_i ≥ \floor{\frac{m - 1}{2}}$ & $\max v_i ≤ \frac{m}{2}$ & ✕ & $\max v_i ≤ \frac{m + 1}{3}$ & $v_1 \mkern-1mu = \mkern-1mu v_2 = \floor{\frac{m - 1}{2}}$\\
		\bottomrule
	\end{tabular}
	\caption{Summary of the results about the class $\PVcl$.
	Each cell specifies those members that satisfy the corresponding property. 
	}
	\label{fig:propsCexplicit}
\end{table}

In front of this incompatibility, the literature seems to favor the minimally Rawlsian principle, as unanimity compromise, the shortlisting rule and the veto-rank rule are minimally Rawlsian. Moreover, within the class of Pareto-and-veto rules, perhaps the most prominent ones, namely those which give both individuals the highest equal or almost equal veto power are minimally Rawlsian. By the established incompatibility, these rules cannot minimize loss dispersion but, except the Pareto-and-veto rule that gives the highest equal veto power, they do not even minimize loss dispersion among the Pareto efficient alternatives that are ranked within the first half of both individuals.

Among the rules we consider, those that minimize loss dispersion are the Pareto-and-veto rules that give each individual a veto power that does not exceed a third of the total number of alternatives. These rules will typically make coarse choices with several tied alternatives. Moreover, they fail two stronger versions of the minimal dispersion condition, one which mandates to pick all minimal dispersion alternatives and the other which mandates to pick only minimal dispersion alternatives.

Therefore, it is of interest to introduce rules that are compatible with the minimal dispersion principle. One possibility is to pick at every preference profile the Pareto efficient alternatives that minimize loss dispersion and only those. This rule is the finite version of Thomson’s [1994]
equal area rule in our framework with no disagreement outcome. By the incompatibility we establish, this rule will be incompatible with the minimal Rawlsian principle. Another possibility that allows to comply with the minimal Rawlsian principle is to pick the Pareto efficient alternatives within the first half of both individuals that minimize loss dispersion. This rule is somehow a counterpart of the veto rank rule that picks the Pareto efficient alternatives within the first half of both individuals that maximize average rank. However, it is more resolute, as it picks at most two alternatives at any given preference profile. Seemingly none of these two rules are considered in the literature and their properties are not known, which suggests that there is room to conceive and analyze new solutions to the two-person social choice problem.

\appendix

\section{Spread measures and minimal dispersion}
\label{sec:spreads}
Recall that we call the dispersion of a loss vector $l$ at $\prof$ the value $d(l) = \abs{l_1 - l_2}$. 

We reuse the following definitions from \citet{cailloux2022compromising}, letting $n$ denote the number of individuals, $l \in \R^n$ denote a generalized loss vector and $\bar{l} = \sum_{i = 1}^n l_i / n$ denote the arithmetic mean of the losses:
\begin{itemize}
	\item the mean absolute difference $\sigma_{mad}(l)= \frac{1}{n^2} \sum_{i = 1}^n\sum_{j = 1}^n \abs{l_i - l_j}$;
	\item the average absolute deviation $\sigma_{ad}(l)= \frac{\sum_{i = 1}^n \abs{l_i - \bar{l}}}{n}$;
	\item the standard deviation $\sigma_{sd}(l)= \sqrt{\frac{\sum_{i = 1}^n(l_i - \bar{l})^2}{n}}$;
	\item the Gini coefficient $\sigma_{G}(l)= \frac{\sum_{i = 1}^n\sum_{j = 1}^n \abs{l_i - l_j}}{2 n \sum_{i = 1}^n l_i}$.
\end{itemize} 

When $n = 2$ as in our case, it is plain that $\forall i \in \set{1, 2}: \abs{l_i - \bar{l}} = \frac{\abs{l_1 - l_2}}{2}$; $\sum_{i = 1}^n\sum_{j = 1}^n \abs{l_i - l_j} = 2 \abs{l_1 - l_2}$; $\forall l \in \R^n: \sigma_{mad}(l) = \sigma_{ad}(l) = \sigma_{sd}(l) = \frac{d(l)}{2}$ and $\sigma_G(l) = \frac{\abs{l_1 - l_2}}{2 (l_1 + l_2)}$. 
Thus, $\sigma_{mad}$, $\sigma_{ad}$ and $\sigma_{sd}$ coincide with $d$, but $\sigma_G$ does not. 
For example, the Gini coefficient considers $(49, 51)$ as less unequal than $(0, 1)$ whereas $d$ orders these vectors reversely.

\bibliography{bibliototal}
\end{document}

