\RequirePackage[l2tabu]{nag}
\documentclass[pagesize, twoside=off, bibliography=totoc, DIV=calc, fontsize=12pt, a4paper]{scrartcl}
\input{preamble/packages}
\input{preamble/redac}
\input{preamble/math_basics}
\input{preamble/math_mine}

%I find these settings useful in draft mode. Should be removed for final versions.
	%Which line breaks are chosen: accept worse lines, therefore reducing risk of overfull lines. Default = 200.
	%\tolerance=2000
	%Accept overfull hbox up to...
	\hfuzz=2cm
	%Reduces verbosity about the bad line breaks.
	\hbadness 5000
	%Reduces verbosity about the underful vboxes.
	\vbadness=1300

\title{Answer to the reviewers}
\author[*]{Olivier Cailloux}
\author[**]{Matías Núñez}
\author[*]{M. Remzi Sanver}
\affil[*]{Université Paris-Dauphine, PSL Research University, CNRS, LAMSADE, 75016 Paris, France.}
\affil[**]{CREST, CNRS, École Polytechnique, GENES, ENSAE Paris, Institut Polytechnique de Paris, 91120 Palaiseau, France.}
\date{}

\hypersetup{
	pdfsubject={},
	pdfkeywords={},
}
\begin{document}
\maketitle

\section{Introduction}
We wish to thank the associate editor and the reviewers for their helpful comments. We have revised the paper accordingly and feel that the paper is now more convincing. In the next pages, we detail our answers to the reviewers’ comments and
how we incorporated their remarks in the paper.


\section{Associate Editor}

The associate editor suggests to try to deal with all comments,
suggestions and questions contained in the two reports.


(S)he also writes: \color{red}In particular, the authors should try to
make some progress in the analysis that Referee 2 proposes at the end of the third paragraph of
his/her report as well as to answer the two questions raised at the end of the report.\color{black}


How should we answer here?




(S)he also makes a list of typos that we have corrected in the paper. Thank you for the suggestions.  






\section{Referee 1}
We thank the reviewer for the positive evaluation and the constructive suggestions.

Here are our replies to the reviewer’s main comments.
\begin{enumerate}[label=({\arabic*})]
  \item We have reorganized the introduction thoroughly.
  \item Our article aims at filling a gap in the literature as much analysis is devoted to the case of three agents or more and the case of two agents is often neglected. It seems to us that returning to the case of more than two agents would hurt the clarity of the paper.
  \item We now present the SCR as a correspondence instead of as a function.
  \item The reviewer is right, the notation $\intvlz{p}$ is simpler than $\intvl{0, p}$ that we used unnecessarily. We have changed the text accordingly.
  \item The notation $\min \max \lprof$ is now in the preliminaries, as suggested. We have also made explicit that the inverse ordering ${\prefiinv}$ is associated to the other individual preferences ${\prefi[\ibar]}$ in Proposition 1.
  \item The definition of Borda winners is given in passing as part of the definition of $\VR$.
  \item We now indicate systematically the preference of each agent in our profiles.
  \item We have completed the sentence.
  \item We chose to keep Definition 1 because of the centrality of this notion and because we have now added a remark following R2’s suggestion that refers to this notion. \commentOC{TODO Def 4: similar IMHO. “all the discussion about the equal loss property could be placed in a footnote.”: I ignore which discussion this refers to.}\commentMN{I think that he refers implies to the notation of loss vectors. I put them in a footnote, please check}
  \item We have completed the tables to avoid blank entries.
  \item \commentOC{Table 1 to be checked?} \commentMN{Checked, please see my comment in Table 1}
  \item \commentOC{Table 2 hyp?} \commentMN{I think that we can when $m\geq 4$, see the paper}.
  \item We have made this consistent.
  \item We have completed the sentence.
\end{enumerate}

\commmentMN{I suggest the following paragraph:}About the other comments: we have implemented all the suggested changes, except for comment (c) regarding the use of symbols $\forall$ and $\exists$. Indeed, after careful examination of the paper, we think that the current use of these symbols is clear and consistent enough (and the symbols are very standard in the literature). We hope that you agree with this point. 




\section{Referee 2}
We thank the reviewer for the evaluation and the constructive suggestions.

We agree that the incompatibility between MR and MD can be viewed as one of the main results in the article. However, we think that exploring the relationship between these axioms and most rules that have been considered in the literature about two agents social choice is also significant. It also helps highlighting how these rules differ. Furthermore, we think that it is interesting to observe that no rule that has been considered in the context of two agents satisfies the MD axiom, an observation which covers, perhaps surprisingly, the well-known Fallback Bargaining rule, which could be superficially considered as very egalitarianism-oriented. 
\commentOC{Dear team, could we try to phrase all of this better together? Should we insist on this in our introduction or conclusion? Should we answer here that we have added a point about that?}

We thank the reviewer for the question about compatibility of $k$-strict Rawlsianism with MD; which has lead to a new remark and footnote (Remark 7 and Footnote 9).

Here are our replies to the reviewer’s main comments.
\begin{enumerate}[label={\alph*})]
  \item We have now specified that $\N$ includes zero.
  \item We have added this observation.
  \item It is in fact equivalent.\commentOC{R2 c: I believe that she is wrong. We could add this to the text, but is it more helpful than confusing? “Note that this is equivalent because $H(P)$ picks the winners among the first $\khalf + 1 = \khalfAlt + 1$ ranks, whose complement to $m$ is $\floor{\frac{m - 1}{2}}$.” This applies similarly to R2 d.} \commentRS{VR and SL are defined for an odd number of alternatives, no?}

  \commentMN{I have been reading the report and I think that the referee might have a point. Observe that he writes "in the formal definitions of the VR correspondence, it is stated that it \emph{selects
among alternatives in H(P) the ones } with the highest Borda scores. However, in
the text it is said that each individual vetoes \emph{her worst (m-1)/2 rounded down
alternatives} before selecting the alternatives with the highest Borda scores." }


\commentMN{I tend to think that he points at an incoherence between the formal definition and the one in the text. Is that it? Do you agree? If you agree, we should simply change the informal definition in the text.}


  
  \item It is in fact equivalent.\commentOC{Could someone confirm that this is true as well?} \commentMN{Again, I think that the referee's point deals with the definitions of $H(P)$ formal and the informal ones in the text. }
\end{enumerate}
\end{document}

